---
title: "Corporate Responsability Versus Easiness of E-Commerce Payments Methods: An Experimental Study"
output:
  html_notebook:
    css: my_style.css
    toc: true
    toc_float: true
    toc_depth: 2
  pdf_document: default
  html_document:
    df_print: paged
    self_contained: false
    css: my_style.css
    toc: true
    toc_float: true
    toc_depth: 2
---


# 1. Introduction

This case study evaluated the impact of adding a new payment method, "ControvPay", on customer perceptions. While such addition was expected to improve convenience, it could also provoke negative reactions due to ethical controversies associated with the provider. To understand this trade-off, we experimentally evaluated the payment method using a range of key metrics:

* Perceived Ease of Use
* Perceived Corporate Social Responsibility
* Purchase Intention
* Customer Loyalty
* Payment Method Adoption

The project's analyses include:

* Data simulation and cleaning
* Exploratory analysis with descriptive statistics and visualizations
* Comparative analyses with linear regression
* Simulation-based predictions

Although based on a real-world project, all data and insights presented here have been simulated to ensure confidentiality.


# 2. Setup

We begin by loading the necessary R packages for data manipulation, visualization, and statistical modeling. 

```{r}

# Data handling
library(dplyr)       # Data manipulation
library(openxlsx)    # Open Excel files

# Visualization
library(ggplot2)     # General plotting
library(vcd)         # Mosaic plots
library(kableExtra)  # Table Formatting
library(beanplot)    # Density distributions


# Statistical analysis
library(psych)       # Descriptive statistics
library(MASS)        # Simulation of multivariate distributions
library(car)         # Scatterplot matrices
library(corrplot)    # Correlation plots
library(effectsize)  # Effect size calculations

```


# 3. Data Simulation

## 3.1. Methodological Brief

The data for this study were collected through a survey experiment. Participants were randomly assigned to one of two conditions. In the first condition, they were shown an anonymous e-commerce platform that included a controversial payment method, ControvPay, alongside other standard options (Credit Card, ChisPay, and MegaPay). The second condition showed the exact same platform but without the ControvPay option. After viewing the platform, participants completed a series of questionnaires about their perceptions and demographic information.


## 3.2. Experimental Assignment

We began our data simulation by creating the random assignment for each customer into two experimental groups:

* Control: Participants in this group viewed a payment page with only the standard payment options (Credit Card, ChisPay, and MegaPay).
* Experimental: Participants in this group viewed the same payment page and options, with the addition of ControvPay.

```{r}

# Set seed for reproducibility
set.seed(123)

# Define dataset size
data.n <- 800

# Initialize dataframe with IDs
pay.df <- data.frame(id = factor(c(1:data.n)))

# Create the factor about the experimental assignment
pay.df$condition <- factor(sample(x = c("control", "experimental"), size = data.n, replace = TRUE))

# Check the data distributions
summary(pay.df)
  
```


## 3.3. Customers' Information

Beyond the basic demographic information, we also simulated a variable that represents the frequency of purchasing in the retailer during the last year. This question was asked together with other questions about purchasing frequency in other retailers to maintain anonymity and add context to the survey. 

```{r}

# Simulate age with a log-normal distribution, capped between 15 and 85
pay.df$age <- round(rlnorm(n = data.n, meanlog = log(40), sdlog = log(1.4)))
pay.df$age[pay.df$age > 85] <- 85
pay.df$age[pay.df$age < 15] <- 15

# Simulate gender
pay.df$gender <- factor(sample(x = c("man", "woman"),
                              size = data.n,
                              replace = TRUE,
                              prob = c(0.5, 0.5)))

# Simulate frequency of purchasing in the retailer within the last year
pay.df$freq.customer <- factor(sample(x = c("none", "1 time", "2-4 times", "5-9 times", "10 times or more"),
                                      size = data.n,
                                      replace = TRUE,
                                      prob = c(0.5, 0.2, 0.15, 0.10, 0.05)
                                      ), 
                               ordered = TRUE, levels = c("none", "1 time", "2-4 times", "5-9 times", "10 times or more")
                               )

# Create a variable to indicate if the participant purchased from the retailer during the last year
pay.df$customer <- rep(NA_real_, data.n)
pay.df$customer [pay.df$freq.customer == "none"] <- 0
pay.df$customer [pay.df$freq.customer %in% c("1 time", "2-4 times", "5-9 times", "10 times or more")] <- 1
pay.df$customer <- as.integer(pay.df$customer)

# Check the data distributions
summary(pay.df)


```


## 3.4. Questionnaire Responses

For each of the dependent variables, we will show the questionnaire items and their data simulation.

For multi-item questionnaires, we simulate the Likert-type items with a function that uses multivariate distributions, with the package MASS

```{r}

# Specify function for the simulation of Likert-type items in a questionnaire

  # Function name: f.sim.likert

  # Input: 
    # n: number of cases to simulate
    # n.items: number of items to simulate
    # mean: mean to simulate for the items
    # sd: standard deviation to simulate for the items
    # rounding: if TRUE, it rounds the scores and keeps them within the scale limits
    # scale.max: maximum score of the items to simulate
    # scale.min: minimun score of the items to simulate
    # corr = correlation to simulate across scale items, 0.6 if nothing is specified

  # Output: a simulated distribution of scores of Likert type items in a scale, using a multivariate distribution with the specified parameters. 

f.sim.likert <- function(n, n.items, mean, sd, rounding = TRUE, scale.max, scale.min, corr = 0.6) {

  # Make sure library MASS is installed and loaded
  if (!requireNamespace("MASS", quietly = TRUE)) {
    install.packages("MASS")
  }
  if (!"package:MASS" %in% search()) {
    library(MASS, quietly = TRUE)
  }
  
  # Specify the correlation matrix
  cor.matrix <- matrix(corr, nrow = n.items, ncol = n.items)
  diag(cor.matrix) <- 1
  
  # Specify the covariance matrix
  cov.matrix <- cor.matrix * (sd^2)
  diag(cov.matrix) <- sd^2
  
  # Simulate correlated scores
  scores <- mvrnorm(n, mu = rep(mean, n.items), Sigma = cov.matrix)
  
  # Rounding and limiting scores if rounding is TRUE
  if(rounding == TRUE) {
    scores <- round(pmin(pmax(scores, scale.min), scale.max))
  }
  return(scores)
}

```

Now we are ready to apply this function to the data simulation of the multi-item scales


### 3.4.1. Perceived Corporate Social Responsibility

The code below shows the questionnaire items used to measure the perception of social responsability of the website. 

```{r}
# Dataframe to display items
measure.sr <- data.frame (Item = c("CSR1", "CSR2", "CSR3", "CSR4"),
                          Text = c("I believe that this retailer ensures that the respect of ethical principles has priority over economic performance.", "I believe that this retailer permits ethical concerns to negatively affect economic performance.", "I believe that this retailer is committed to well-defined ethics principles.", "I believe that this retailer avoids compromising ethical standards in order to achieve corporate goals.")) 

# 4. Conversion of the items dataframe to a table, including the measure description

kable(measure.sr, "html", booktabs = TRUE,
      caption = "Table 1. Perception of Social Responsibility") %>%
  add_footnote(
    label = "Note: The items were adapted from the scale by Maignan (2001). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree)",
    notation = "none"
  )

```

We simulate the responses to the social responsability items with slightly lower responses in the experimental group, but only within those who are customers of the retailer. 

```{r}

# Use function in section 3.4 to simulate a preliminary distribution of scores (without any experimental effect)
csr.scores <- f.sim.likert(n = data.n, 
                           n.items = 4,
                           mean = 5.5, 
                           sd = 1.5,
                           rounding = FALSE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)

# Apply higher scores for the customers group assigned to the experimental group
effect.size <- 0.3 
csr.scores [pay.df$condition == "experimental" & pay.df$customer == 1] <- 
  csr.scores [pay.df$condition == "experimental" & pay.df$customer == 1] - 
  effect.size

# Round the scores and constrain them within the scale limits
csr.scores <- round(pmin(pmax(csr.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$csr1 <- csr.scores[, 1]
pay.df$csr2 <- csr.scores[, 2]
pay.df$csr3 <- csr.scores[, 3]
pay.df$csr4 <- csr.scores[, 4]

##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(2,2))

# Create histograms for each item
barplot(table(pay.df$csr1))
barplot(table(pay.df$csr2))
barplot(table(pay.df$csr3))
barplot(table(pay.df$csr4))

# Correlations across items
corr.test(pay.df[, c("csr1", "csr2", "csr3", "csr4")])

# Item scores across condition and customer groups
aggregate(pay.df$csr1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$csr2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$csr3, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$csr4, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)

```

The simulation is performed as expected, with a tendency to respond slightly lower for customers in the experimental condition. 


### 3.4.2. Perceived Ease of Use

The code below shows the questionnaire items used to measure the expected ease for the payment process. 

```{r}

# Dataframe to display items
measure.eou <- data.frame(
  Item = c("EOU1", "EOU2", "EOU3", "EOU4"),
  Text = c(
    "My interaction with the payment service will be clear and understandable.",
    "Interacting with the payment service will not require a lot of my mental effort.",
    "I expect to find the payment service easy to use.",
    "I expect to find it easy to get the payment service to do what I want it to do."
  )
) 

# Create the table
kable(measure.eou, format = "html", 
      caption = "Table 2. Perceived Ease of Use")  %>%
  add_footnote(
    label = "Note: The items were adapted from the Ease of Use scale by Venkatesh & Davis (2000). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree)",
    notation = "none"
  )

```


We simulate the responses to the ease of use items as totally independent of the experimental condition, and inversely correlated with age

```{r}

# Use function in section 3.4 to simulate a preliminary distribution of scores (without any experimental effect)
eou.scores <- f.sim.likert(n = data.n, 
                           n.items = 4,
                           mean = 5, 
                           sd = 1.6,
                           rounding = TRUE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)

# Apply higher scores for younger customers
age.effect.size <- 0.04 

for(i in 1:ncol(eou.scores)) {
  eou.scores[, i] <- eou.scores[, i] - pay.df$age * age.effect.size
}

# Round the scores and constrain them within the scale limits
eou.scores <- round(pmin(pmax(eou.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$eou1 <- eou.scores[, 1]
pay.df$eou2 <- eou.scores[, 2]
pay.df$eou3 <- eou.scores[, 3]
pay.df$eou4 <- eou.scores[, 4]

##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(2,2))

# Create histograms for each item
barplot(table(pay.df$eou1))
barplot(table(pay.df$eou2))
barplot(table(pay.df$eou3))
barplot(table(pay.df$eou4))

# Correlations across items
corr.test(pay.df[, c("eou1", "eou2", "eou3", "eou4")])

# Item scores across condition and customer groups
aggregate(pay.df$eou1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$eou2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$eou3, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$eou4, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)


```


### 3.4.3. Purchase Intention

The code below shows the questionnaire items used to measure the intention to purchase after seeing the payment options. 

```{r}

# Dataframe to display items
measure.pi <- data.frame(
  Item = c("PI1", "PI2"),
  Text = c(
    "I would intend to use the payment options.",
    "I predict that I would use the payment options."
  )
) 

kable(measure.pi, format = "html", 
      caption = "Table 3. Purchase Intention")  %>%
  add_footnote(
    label = "Note: The items were adapted from the Intention to Purchase scale by Venkatesh & Davis (2000). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree)",
    notation = "none"
  )

```

We simulate the responses to the purchase intention items as moderately related to the perceived ease of use and slightly related to the perception of social responsability.

```{r}
# Use function in section 3.4 to simulate a preliminary distribution of scores
pi.scores <- f.sim.likert(n = data.n, 
                           n.items = 2,
                           mean = 5, 
                           sd = 1.2,
                           rounding = FALSE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)
##
# Apply the relationship with ease of use and social responsability perceptions
##

# Define vectors for the standardized means of ease of use and social responsability
csr.mean <- scale(rowMeans(pay.df[, c("csr1", "csr2", "csr3", "csr4")]))
eou.mean <- scale(rowMeans(pay.df[, c("eou1", "eou2", "eou3", "eou4")]))

# Define the effect sizes for perceptions of easiness and social responsability
csr.effect.size <- 0.1
eou.effect.size <- 0.3 

# Apply the effects to each item
for(i in 1:ncol(pi.scores)) {
  pi.scores[, i] <- pi.scores[, i] + csr.mean * csr.effect.size + eou.mean * eou.effect.size
}

# Round the scores and constrain them within the scale limits
pi.scores <- round(pmin(pmax(pi.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$pi1 <- pi.scores[, 1]
pay.df$pi2 <- pi.scores[, 2]


##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(1,2))

# Create histograms for each item
barplot(table(pay.df$pi1))
barplot(table(pay.df$pi2))

# Correlations across items
corr.test(pay.df[, c("pi1", "pi2")])

# Item scores across condition and customer groups
aggregate(pay.df$pi1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$pi2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)

```


### 3.4.4. Customer Loyalty

The code below shows the questionnaire items used to measure customer loyalty after seeing the payment options. 

```{r}

# Dataframe to display items
# Customer Loyalty
measure.cl <- data.frame(
  Item = c("CL1", "CL2"),
  Text = c(
    "I will likely visit the website in the future.",
    "How likely are you to recommend the website to a friend or colleague?"
  )
)

kable(measure.cl, format = "html", 
      caption = "Table 4. Cutomer Loyalty")  %>%
  add_footnote(
    label = "Note: The items were adapted from the Loyalty Scale of the SUPR-Q (Sauro, 2015). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree) for CL1, and from 1 (Not at all likely) to 7 (extremely likely) for CL2",
    notation = "none"
  )

```


We simulate the responses to the purchase intention items as moderately related to both perceived ease of use and the perception of social responsability.


```{r}
# Use function in section 3.4 to simulate a preliminary distribution of scores
cl.scores <- f.sim.likert(n = data.n, 
                           n.items = 2,
                           mean = 4.2, 
                           sd = 1.5,
                           rounding = FALSE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)
##
# Apply higher scores for the customers group assigned to the experimental group
##

# In section 3.4.3 we already defined the vectors with the means for ease of use (eou_mean) and social responsability (csr_mean)

# Define the effect sizes for perceptions of easiness and social responsability
csr.effect.size <- 0.6
eou.effect.size <- 0.6

# Apply the effects to each item
for(i in 1:ncol(cl.scores)) {
  cl.scores[, i] <- cl.scores[, i] + csr.mean * csr.effect.size + eou.mean * eou.effect.size
}

# Round the scores and constrain them within the scale limits
cl.scores <- round(pmin(pmax(cl.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$cl1 <- cl.scores[, 1]
pay.df$cl2 <- cl.scores[, 2]


##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(1,2))

# Create histograms for each item
barplot(table(pay.df$cl1))
barplot(table(pay.df$cl2))

# Correlations across items
corr.test(pay.df[, c("cl1", "cl2")])

# Item scores across condition and customer groups
aggregate(pay.df$cl1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$cl2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)


```


### 3.4.5. Payment Method Adoption

The level of adoption of ControvPay was measured at the end of the survey with question that asked participants which method they would choose among the ones presented. For the analyses, we simulate those who selected ControvPay in the experimental condition, setting lower probabilities to select it if participants provided low scores for social responsability. 

```{r}

#Set a reference probability for customers not affected by social responsability issues
prob.adoption <- rep (0.15, data.n)

# Reduce the probability for those in the experimental condition who scored low in social responability
prob.adoption [pay.df$condition == "experimental" & csr.mean <= 3] <- 0.05

# Create the variable for adoption
pay.df$adoption <- rbinom(n = data.n, size = 1, prob = prob.adoption)

# Set the value to NA for the control condition, since they were not offered the option to choose ControvPay
pay.df$adoption [pay.df$condition == "control"] <- NA_real_

# Check the distribution
with(pay.df, table(adoption, condition))

```


# 4. Reliability Analyses

We use Cronbach's Alpha to evaluate the internal reliability of the multi-item questionnaire (social responsability, percepcion of ease of use, purchase intention, and loyalty). 


```{r}

# Social responsability
rel.csr <- alpha(x= pay.df [ , c("csr1", "csr2", "csr3", "csr4")])
summary(rel.csr)

# Ease of use
rel.eou <- alpha(x= pay.df [ , c("eou1", "eou2", "eou3", "eou4")])
summary(rel.eou)

# Purchase intention
rel.pi <- alpha(x= pay.df [ , c("pi1", "pi2")])
summary(rel.pi)

# Customer Loyalty
rel.cl <- alpha(x= pay.df [ , c("cl1", "cl2")])
summary(rel.cl)


```

The four scales show acceptable levels of internal reliability (Cronbach's Alpha > 0.70), so we proceed to calculate the average of the items in each scale as single scale measurements. 

```{r}

# Create variables with the average of the scales' items
pay.df$social.responsability <- rowMeans(pay.df[, c("csr1", "csr2", "csr3", "csr4")])
pay.df$ease <- rowMeans(pay.df[, c("eou1", "eou2", "eou3", "eou4")])
pay.df$purchase.intention <- rowMeans(pay.df[, c("pi1", "pi2")])
pay.df$loyalty <- rowMeans(pay.df[, c("cl1", "cl2")])

# Move the item variables to another dataset to keep the main database cleaner
# Correct using base R
item.names <- c("csr1", "csr2", "csr3", "csr4", "eou1", "eou2", "eou3", "eou4", "pi1", "pi2", "cl1", "cl2")
items.df <- pay.df[, (names(pay.df) %in% item.names)]
pay.df <- pay.df[, !(names(pay.df) %in% item.names)]

# Check the dataset
summary(pay.df)
hist(pay.df$social.responsability)
hist(pay.df$ease)
hist(pay.df$purchase.intention)
hist(pay.df$loyalty)


```



# 5. Sample Demographics

To obtain a comprehensive summary of our sample, we applied: 

* the summary() function, which provides frequencies for our factor variables
* the describe() function from the psych package, which provides means, standard deviations and other statistics for numeric variables. We can also look at the mean for categorical variables as indicators of the proportions. 

```{r}
# Information for numeric variables
describe(pay.df)

# Information for categorical variables
summary(pay.df)

```

The sample results indicated that: 
 * gender categories were evenly distributed across our sample, with approximate 50% of men and 50% of women. 
 * The average age of participants is 43 years (sd = 14.41), varying within 85 and 16 years. 
 * Half of the sample are customers from the retailer, who at least bought one time to the retailer in the last year. 
 * The sample is evenly assigned to the control and the experimental condition, each group composing 50% of participants. 
 
Yet, to make sure the results we obtained about the comparison across customers and experimental groups are reliable, we needed to check for demotragphic differences across those groups and the potential effect of the demographic variables on our outcomes. 


# 6. Checks for Balanced Comparisons

## 6.1. Balance in Experimental Assignment

We assessed whether the control and experimental groups differed on age, gender, or customer status using descriptive statistics, visualizations, and statistical tests (chi-square tests for categorical variables, independent t-tests for age).

```{r}

# Obtain general descriptives by experimental condition
describeBy(pay.df[, c("age", "gender", "customer")], group = pay.df$condition)

# Check for statistical differences in age with an independent samples t-test
t.test(age ~ condition, data = pay.df)
cohens_d(age ~ condition, data = pay.df)

# Check for statistical differences in gender with a chi square test
table.gender.condition <- with (pay.df, table(gender,condition))
chisq.test(table.gender.condition)

# Check for statistical differences in customers ratio with a chi-square test
table.customer.condition <- with (pay.df, table(customer,condition))
chisq.test(table.customer.condition)


# Obtain visualizations

par(mfrow = c(1, 3))
boxplot(age ~ condition, data = pay.df, main = "Age by Condition")
barplot(table.gender.condition, beside = TRUE, main = "Gender Distribution")
barplot(table.customer.condition, beside = TRUE, main = "Gender Distribution")
par(mfrow = c(1, 1))

```

The two experimental gropus are similar in terms of age, gender, and customers ratio. Yet, since we are also considering being a customer as a potential interaction factor, we also check the assignment balance within customers and non customer.


## 6.2. Balance in Customers Groups

We assessed whether the customer groups within the control and experimental groups differed on age and gender using descriptive statistics, visualizations, and statistical tests (chi-square test for gender, factorial ANOVA test for age).

```{r}

# Obtain general descriptives by condition and customer groups
describeBy(pay.df[, c("age", "gender")], group = list(pay.df$condition, pay.df$customer))

# Factorial ANOVA for testing differences across age
age_anova <- aov(age ~ condition * customer, data = pay.df)
summary(age_anova)
age.eta.squared <- eta_squared(age_anova, partial = TRUE) 
age.eta.squared

# Chi-square for genders  
# We first create a variable grouping participants by both experimental group and customer group
pay.df$condition.customer <- rep(NA_character_, nrow(pay.df))
pay.df$condition.customer [pay.df$condition == "experimental" & pay.df$customer == 1] <- "exp.customers"
pay.df$condition.customer [pay.df$condition == "experimental" & pay.df$customer == 0] <- "exp.non.customers"
pay.df$condition.customer [pay.df$condition == "control" & pay.df$customer == 1] <- "ct.customers"
pay.df$condition.customer [pay.df$condition == "control" & pay.df$customer == 0] <- "ct.non.customers"
pay.df$condition.customer <- factor(pay.df$condition.customer)


# Chi-square
table.gender.condition.customer <- with (pay.df, table(gender, condition.customer))
chisq.test(table.gender.condition.customer)


# Visualization for the four groups

# Set more margins in the bottom
par(mar = c(8, 4.1, 4.1, 2.1)) 

# Age by 2x2 groups
boxplot(age ~ condition.customer, data = pay.df,
        main = "Age Distribution by Condition × Customer",
        las = 2) # Rotate x-axis labels



# Gender proportions by 2x2 groups
barplot(table.gender.condition.customer, beside = TRUE,
        main = "Gender by Condition × Customer",
        legend.text = TRUE)

par(mar = c(5.1, 4.1, 4.1, 2.1)) 

```

The factorial ANOVA revealed no significant interaction between condition and customer status for age (F(1, 796) = X.XX, p = .XXX), and the chi-square test showed no significant association between the combined condition-customer groups and gender distribution (χ²(3) = X.XX, p = .XXX). This indicates successful balance across all four experimental cells, supporting the internal validity of subsequent comparisons

Yet, the comparisons can become more rigorous if we also account for potential effects of the demographic variables in our outcomes, as we can always expect some level of unbalance between conditions even if differences were not significant. 


## 6.2. Control of Demographics Effects

To identify any relevant effect on the demographic variables on the outcomes, we evaluate the correlations between these two types of variables, which we can observe in the correlation matrix, in a scatterplot matrix or in a correlation plot. 

```{r}
# Extract a dataframe with the variables to correlate
cor.df <- pay.df [ , c("age", "gender", "condition", "customer", "social.responsability", "ease", "purchase.intention", "loyalty")]
cor.df$gender <- as.numeric(ifelse(cor.df$gender == "woman", 0,1))
cor.df$condition <- as.numeric(ifelse(cor.df$condition == "control", 0,1))


# Correlation matrix 
corr.test (cor.df, use = "complete.obs")

# Scatterplot matrix
scatterplotMatrix (cor.df, use = "complete.obs")

# Correlation plot
corrplot.mixed(corr = cor(cor.df, use = "complete.obs"), upper = "ellipse")
```

Correlation analysis revealed that age was significantly associated with ease of use (r = -0.XX, p < .001), purchase intention (r = -0.XX, p < .001), and loyalty (r = -0.XX, p < .001). In contrast, gender showed no significant correlations with any outcome variables (all p > .05). Based on these findings, age will be included as a covariate in sensitivity analyses involving the affected outcome variables.


# 7. Experimental Effects Analysis

In this section, we evaluate the causal impact of exposing participants to ControvPay versus traditional payment methods only. We also examine whether these experimental effects vary depending on participants' customer status (current customers vs. non-customers).

To ensure the validity of our causal inferences, we first verify that the random assignment created balanced comparison groups on key demographic variables.











To evaluate the causal impact of exposing participants to ControvPay versus traditional payment methods only, we started employing a 2×2 factorial Analysis of Variance (ANCOVA). This design allowed us to test both the main effect of the experimental condition and its potential interaction with participants' customer status (current customers vs. non-customers of the retailer), while controlling for potential confounding effects of age and gender as covariates.

Specifically, the analysis addresses three key questions:

* 1. Does the presence of ControvPay influence consumer perceptions and intentions?
* 2. Do these effects differ between existing customers and non-customers?
* 3. How robust are these findings when accounting for demographic covariates?


## 5.1. Check of Normality Assumption







