---
title: "Corporate responsibility Versus Easiness of E-Commerce Payments Methods: An Experimental Study"
output:
  html_notebook:
    css: my_style.css
    toc: true
    toc_float: true
    toc_depth: 2
  pdf_document: default
  html_document:
    df_print: paged
    self_contained: false
    css: my_style.css
    toc: true
    toc_float: true
    toc_depth: 2
---


# 1. Introduction

This case study evaluated the impact of adding a new payment method, "ControvPay", on customer perceptions. While such addition was expected to improve convenience, it could also provoke negative reactions due to ethical controversies associated with the provider. To understand this trade-off, we experimentally evaluated the payment method using a range of key metrics:

* Perceived Ease of Use
* Perceived Corporate Social Responsibility
* Purchase Intention
* Customer Loyalty
* Payment Method Adoption

The project's analyses include:

* Data simulation and cleaning. 
* Reliability analysis. 
* Exploratory analysis with descriptive statistics, visualizations. 
* Balanced-comparison checks with basic inferential tests (chi-square, t-test, ANOVA, correlations). 
* Comparative analyses with factorial ANOVA and ANCOVA models. 
* Sensitivity analyses with Bayesian modeling. 
* Simulation-based predictions

Although based on a real-world project, all data and insights presented here have been simulated to ensure confidentiality.


# 2. Setup

We begin by loading the necessary R packages for data manipulation, visualization, and statistical modeling. 

```{r}

# Data handling
library(dplyr)       # Data manipulation
library(openxlsx)    # Open Excel files

# Visualization
library(ggplot2)     # General plotting
library(vcd)         # Mosaic plots
library(kableExtra)  # Table Formatting
library(beanplot)    # Density distributions


# Statistical analysis
library(psych)       # Descriptive statistics
library(MASS)        # Simulation of multivariate distributions
library(car)         # Scatterplot matrices
library(corrplot)    # Correlation plots
library(effectsize)  # Effect size calculations
library(BayesFactor) # For Bayesian inference

# PACKAGE USED FOR MEDIATION ANALYSES
# For mediation analyses we used the application Process for R, freely available with instructions at: https://www.processmacro.org/index.html 

```


# 3. Data Simulation

## 3.1. Methodological Brief

The data for this study were collected through a survey experiment. Participants were randomly assigned to one of two conditions. In the first condition, they were shown an anonymous e-commerce platform that included a controversial payment method, ControvPay, alongside other standard options (Credit Card, ChisPay, and MegaPay). The second condition showed the exact same platform but without the ControvPay option. After viewing the platform, participants completed a series of questionnaires about their perceptions and demographic information.


## 3.2. Experimental Assignment

We began our data simulation by creating the random assignment for each customer into two experimental groups:

* Control: Participants in this group viewed a payment page with only the standard payment options (Credit Card, ChisPay, and MegaPay).
* Experimental: Participants in this group viewed the same payment page and options, with the addition of ControvPay.

```{r}

# Set seed for reproducibility
set.seed(123)

# Define dataset size
data.n <- 800

# Initialize dataframe with IDs
pay.df <- data.frame(id = factor(c(1:data.n)))

# Create the factor about the experimental assignment
pay.df$condition <- factor(sample(x = c("control", "experimental"), size = data.n, replace = TRUE))

# Check the data distributions
summary(pay.df)
  
```


## 3.3. Participants' Information

Beyond the basic demographic information, we also simulated a variable that represents the frequency of purchasing in the retailer during the last year. This question was asked together with other questions about purchasing frequency in other retailers to maintain anonymity and add context to the survey. 

```{r}

# Simulate age with a log-normal distribution, capped between 15 and 85
pay.df$age <- round(rlnorm(n = data.n, meanlog = log(40), sdlog = log(1.4)))
pay.df$age[pay.df$age > 85] <- 85
pay.df$age[pay.df$age < 15] <- 15

# Simulate gender
pay.df$gender <- factor(sample(x = c("man", "woman"),
                              size = data.n,
                              replace = TRUE,
                              prob = c(0.5, 0.5)))

# Simulate frequency of purchasing in the retailer within the last year
pay.df$freq.customer <- factor(sample(x = c("none", "1 time", "2-4 times", "5-9 times", "10 times or more"),
                                      size = data.n,
                                      replace = TRUE,
                                      prob = c(0.5, 0.2, 0.15, 0.10, 0.05)
                                      ), 
                               ordered = TRUE, levels = c("none", "1 time", "2-4 times", "5-9 times", "10 times or more")
                               )

# Create a variable to indicate if the participant purchased from the retailer during the last year
pay.df$customer <- rep(NA_real_, data.n)
pay.df$customer [pay.df$freq.customer == "none"] <- "no"
pay.df$customer [pay.df$freq.customer %in% c("1 time", "2-4 times", "5-9 times", "10 times or more")] <- "yes"
pay.df$customer <- factor (pay.df$customer)


# Check the data distributions
summary(pay.df)


```


## 3.4. Questionnaire Responses

For each of the dependent variables, we will show the questionnaire items and their data simulation.

For multi-item questionnaires, we simulate the Likert-type items with a function that uses multivariate distributions, with the package MASS

```{r}

# Specify function for the simulation of Likert-type items in a questionnaire

  # Function name: f.sim.likert

  # Input: 
    # n: number of cases to simulate
    # n.items: number of items to simulate
    # mean: mean to simulate for the items
    # sd: standard deviation to simulate for the items
    # rounding: if TRUE, it rounds the scores and keeps them within the scale limits
    # scale.max: maximum score of the items to simulate
    # scale.min: minimun score of the items to simulate
    # corr = correlation to simulate across scale items, 0.6 if nothing is specified

  # Output: a simulated distribution of scores of Likert type items in a scale, using a multivariate distribution with the specified parameters. 

f.sim.likert <- function(n, n.items, mean, sd, rounding = TRUE, scale.max, scale.min, corr = 0.6) {

  # Make sure library MASS is installed and loaded
  if (!requireNamespace("MASS", quietly = TRUE)) {
    install.packages("MASS")
  }
  if (!"package:MASS" %in% search()) {
    library(MASS, quietly = TRUE)
  }
  
  # Specify the correlation matrix
  cor.matrix <- matrix(corr, nrow = n.items, ncol = n.items)
  diag(cor.matrix) <- 1
  
  # Specify the covariance matrix
  cov.matrix <- cor.matrix * (sd^2)
  diag(cov.matrix) <- sd^2
  
  # Simulate correlated scores
  scores <- mvrnorm(n, mu = rep(mean, n.items), Sigma = cov.matrix)
  
  # Rounding and limiting scores if rounding is TRUE
  if(rounding == TRUE) {
    scores <- round(pmin(pmax(scores, scale.min), scale.max))
  }
  return(scores)
}

```

Now we are ready to apply this function to the data simulation of the multi-item scales


### 3.4.1. Perceived Corporate Social Responsibility

The code below shows the questionnaire items used to measure the perception of social responsibility of the website. 

```{r}
# Dataframe to display items
measure.sr <- data.frame (Item = c("CSR1", "CSR2", "CSR3", "CSR4"),
                          Text = c("I believe that this retailer ensures that the respect of ethical principles has priority over economic performance.", "I believe that this retailer permits ethical concerns to negatively affect economic performance.", "I believe that this retailer is committed to well-defined ethics principles.", "I believe that this retailer avoids compromising ethical standards in order to achieve corporate goals.")) 

# 4. Conversion of the items dataframe to a table, including the measure description

kable(measure.sr, "html", booktabs = TRUE,
      caption = "Table 1. Perception of Social Responsibility") %>%
  add_footnote(
    label = "Note: The items were adapted from the scale by Maignan (2001). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree)",
    notation = "none"
  )

```

We simulate the responses to the social responsibility items with slightly lower responses in the experimental group, but only within those who are customers of the retailer. 

```{r}

# Use function in section 3.4 to simulate a preliminary distribution of scores (without any experimental effect)
csr.scores <- f.sim.likert(n = data.n, 
                           n.items = 4,
                           mean = 5.5, 
                           sd = 1.5,
                           rounding = FALSE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)

# Apply higher scores for the customers group assigned to the experimental group
effect.size <- 0.35 
csr.scores [pay.df$condition == "experimental" & pay.df$customer == "yes"] <- 
  csr.scores [pay.df$condition == "experimental" & pay.df$customer == "yes"] - 
  effect.size

# Round the scores and constrain them within the scale limits
csr.scores <- round(pmin(pmax(csr.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$csr1 <- csr.scores[, 1]
pay.df$csr2 <- csr.scores[, 2]
pay.df$csr3 <- csr.scores[, 3]
pay.df$csr4 <- csr.scores[, 4]

##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(2,2))

# Create histograms for each item
barplot(table(pay.df$csr1))
barplot(table(pay.df$csr2))
barplot(table(pay.df$csr3))
barplot(table(pay.df$csr4))

# Correlations across items
corr.test(pay.df[, c("csr1", "csr2", "csr3", "csr4")])

# Item scores across condition and customer groups
aggregate(pay.df$csr1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$csr2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$csr3, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$csr4, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)

```

The simulation is performed as expected, with a tendency to respond slightly lower for customers in the experimental condition. 


### 3.4.2. Perceived Ease of Use

The code below shows the questionnaire items used to measure the expected ease for the payment process. 

```{r}

# Dataframe to display items
measure.eou <- data.frame(
  Item = c("EOU1", "EOU2", "EOU3", "EOU4"),
  Text = c(
    "My interaction with the payment service will be clear and understandable.",
    "Interacting with the payment service will not require a lot of my mental effort.",
    "I expect to find the payment service easy to use.",
    "I expect to find it easy to get the payment service to do what I want it to do."
  )
) 

# Create the table
kable(measure.eou, format = "html", 
      caption = "Table 2. Perceived Ease of Use")  %>%
  add_footnote(
    label = "Note: The items were adapted from the Ease of Use scale by Venkatesh & Davis (2000). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree)",
    notation = "none"
  )

```


We simulate the responses to the ease of use items as totally independent of the experimental condition, and inversely correlated with age

```{r}

# Use function in section 3.4 to simulate a preliminary distribution of scores (without any experimental effect)
eou.scores <- f.sim.likert(n = data.n, 
                           n.items = 4,
                           mean = 5, 
                           sd = 1.6,
                           rounding = TRUE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)

# Apply higher scores for younger customers
age.effect.size <- 0.04 

for(i in 1:ncol(eou.scores)) {
  eou.scores[, i] <- eou.scores[, i] - pay.df$age * age.effect.size
}

# Round the scores and constrain them within the scale limits
eou.scores <- round(pmin(pmax(eou.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$eou1 <- eou.scores[, 1]
pay.df$eou2 <- eou.scores[, 2]
pay.df$eou3 <- eou.scores[, 3]
pay.df$eou4 <- eou.scores[, 4]

##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(2,2))

# Create histograms for each item
barplot(table(pay.df$eou1))
barplot(table(pay.df$eou2))
barplot(table(pay.df$eou3))
barplot(table(pay.df$eou4))

# Correlations across items
corr.test(pay.df[, c("eou1", "eou2", "eou3", "eou4")])

# Item scores across condition and customer groups
aggregate(pay.df$eou1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$eou2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$eou3, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$eou4, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)


```


### 3.4.3. Purchase Intention

The code below shows the questionnaire items used to measure the intention to purchase after seeing the payment options. 

```{r}

# Dataframe to display items
measure.pi <- data.frame(
  Item = c("PI1", "PI2"),
  Text = c(
    "I would intend to use the payment options.",
    "I predict that I would use the payment options."
  )
) 

kable(measure.pi, format = "html", 
      caption = "Table 3. Purchase Intention")  %>%
  add_footnote(
    label = "Note: The items were adapted from the Intention to Purchase scale by Venkatesh & Davis (2000). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree)",
    notation = "none"
  )

```

We simulate the responses to the purchase intention items as moderately related to the perceived ease of use and slightly related to the perception of social responsibility.

```{r}
# Use function in section 3.4 to simulate a preliminary distribution of scores
pi.scores <- f.sim.likert(n = data.n, 
                           n.items = 2,
                           mean = 5, 
                           sd = 1.2,
                           rounding = FALSE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)
##
# Apply the relationship with ease of use and social responsibility perceptions
##

# Define vectors for the standardized means of ease of use and social responsibility
csr.mean <- scale(rowMeans(pay.df[, c("csr1", "csr2", "csr3", "csr4")]))
eou.mean <- scale(rowMeans(pay.df[, c("eou1", "eou2", "eou3", "eou4")]))

# Define the effect sizes for perceptions of easiness and social responsibility
csr.effect.size <- 0.1
eou.effect.size <- 0.3 

# Apply the effects to each item
for(i in 1:ncol(pi.scores)) {
  pi.scores[, i] <- pi.scores[, i] + csr.mean * csr.effect.size + eou.mean * eou.effect.size
}

# Round the scores and constrain them within the scale limits
pi.scores <- round(pmin(pmax(pi.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$pi1 <- pi.scores[, 1]
pay.df$pi2 <- pi.scores[, 2]


##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(1,2))

# Create histograms for each item
barplot(table(pay.df$pi1))
barplot(table(pay.df$pi2))

# Correlations across items
corr.test(pay.df[, c("pi1", "pi2")])

# Item scores across condition and customer groups
aggregate(pay.df$pi1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$pi2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)

```


### 3.4.4. Customer Loyalty

The code below shows the questionnaire items used to measure customer loyalty after seeing the payment options. 

```{r}

# Dataframe to display items
# Customer Loyalty
measure.cl <- data.frame(
  Item = c("CL1", "CL2"),
  Text = c(
    "I will likely visit the website in the future.",
    "How likely are you to recommend the website to a friend or colleague?"
  )
)

kable(measure.cl, format = "html", 
      caption = "Table 4. Cutomer Loyalty")  %>%
  add_footnote(
    label = "Note: The items were adapted from the Loyalty Scale of the SUPR-Q (Sauro, 2015). Participants responded with a Likert-type scale from 1 (strongly disagree) to 7 (completely agree) for CL1, and from 1 (Not at all likely) to 7 (extremely likely) for CL2",
    notation = "none"
  )

```


We simulate the responses to the purchase intention items as moderately related to both perceived ease of use and the perception of social responsibility.


```{r}
# Use function in section 3.4 to simulate a preliminary distribution of scores
cl.scores <- f.sim.likert(n = data.n, 
                           n.items = 2,
                           mean = 4.2, 
                           sd = 1.4,
                           rounding = FALSE,
                           scale.max = 7,
                           scale.min = 1, 
                           corr = 0.6)
##
# Apply higher scores for the customers group assigned to the experimental group
##

# In section 3.4.3 we already defined the vectors with the means for ease of use (eou_mean) and social responsibility (csr_mean)

# Define the effect sizes for perceptions of easiness and social responsibility
csr.effect.size <- 0.7
eou.effect.size <- 0.6

# Apply the effects to each item
for(i in 1:ncol(cl.scores)) {
  cl.scores[, i] <- cl.scores[, i] + csr.mean * csr.effect.size + eou.mean * eou.effect.size
}

# Round the scores and constrain them within the scale limits
cl.scores <- round(pmin(pmax(cl.scores, 1), 7))

# Assign the scores to dataframe variables
pay.df$cl1 <- cl.scores[, 1]
pay.df$cl2 <- cl.scores[, 2]


##
# Check the distributions
##

# Set the graph objects to a 2x2 format
par(mfrow =c(1,2))

# Create histograms for each item
barplot(table(pay.df$cl1))
barplot(table(pay.df$cl2))

# Correlations across items
corr.test(pay.df[, c("cl1", "cl2")])

# Item scores across condition and customer groups
aggregate(pay.df$cl1, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)
aggregate(pay.df$cl2, by = list (condition = pay.df$condition, customer = pay.df$customer), mean)


```


### 3.4.5. Payment Method Adoption

The level of adoption of ControvPay was measured at the end of the survey with question that asked participants which method they would choose among the ones presented. For the analyses, we simulate those who selected ControvPay in the experimental condition, setting lower probabilities to select it if participants provided low scores for social responsibility. 

```{r}

#Set a reference probability for customers not affected by social responsibility issues
prob.adoption <- rep (0.15, data.n)

# Reduce the probability for those in the experimental condition who scored low in social responability
prob.adoption [pay.df$condition == "experimental" & csr.mean <= 3] <- 0.05

# Create the variable for adoption
pay.df$adoption <- rbinom(n = data.n, size = 1, prob = prob.adoption)

# Set the value to NA for the control condition, since they were not offered the option to choose ControvPay
pay.df$adoption [pay.df$condition == "control"] <- NA_real_

# Check the distribution
with(pay.df, table(adoption, condition))

```
*******revisar*****
******
******


# 4. Reliability Analyses

We use Cronbach's Alpha to evaluate the internal reliability of the multi-item questionnaire (social responsibility, percepcion of ease of use, purchase intention, and loyalty). 


```{r}

# Social responsibility
rel.csr <- alpha(x= pay.df [ , c("csr1", "csr2", "csr3", "csr4")])
summary(rel.csr)

# Ease of use
rel.eou <- alpha(x= pay.df [ , c("eou1", "eou2", "eou3", "eou4")])
summary(rel.eou)

# Purchase intention
rel.pi <- alpha(x= pay.df [ , c("pi1", "pi2")])
summary(rel.pi)

# Customer Loyalty
rel.cl <- alpha(x= pay.df [ , c("cl1", "cl2")])
summary(rel.cl)


```

The four scales show acceptable levels of internal reliability (Cronbach's Alpha > 0.70), so we proceed to calculate the average of the items in each scale as single scale measurements. 

```{r}

# Create variables with the average of the scales' items
pay.df$social.responsibility <- rowMeans(pay.df[, c("csr1", "csr2", "csr3", "csr4")])
pay.df$ease <- rowMeans(pay.df[, c("eou1", "eou2", "eou3", "eou4")])
pay.df$purchase.intention <- rowMeans(pay.df[, c("pi1", "pi2")])
pay.df$loyalty <- rowMeans(pay.df[, c("cl1", "cl2")])

# Move the item variables to another dataset to keep the main database cleaner
# Correct using base R
item.names <- c("csr1", "csr2", "csr3", "csr4", "eou1", "eou2", "eou3", "eou4", "pi1", "pi2", "cl1", "cl2")
items.df <- pay.df[, (names(pay.df) %in% item.names)]
pay.df <- pay.df[, !(names(pay.df) %in% item.names)]

# Check the dataset
summary(pay.df)



```



# 5. Sample Demographics

To obtain a comprehensive summary of our sample, we applied: 

* the summary() function, which provides frequencies for our factor variables
* the describe() function from the psych package, which provides means, standard deviations and other statistics for numeric variables. We can also look at the mean for categorical variables as indicators of the proportions. 

```{r}
# Information for numeric variables
describe(pay.df)

# Information for categorical variables
summary(pay.df)

```

The sample results indicated that: 
 * gender categories were evenly distributed across our sample, with approximate 50% of men and 50% of women. 
 * The average age of participants is 43 years (sd = 14.41), varying within 85 and 16 years. 
 * Half of the sample are customers from the retailer, who at least bought one time to the retailer in the last year. 
 * The sample is evenly assigned to the control and the experimental condition, each group composing 50% of participants. 
 
Yet, to make sure the results we obtained about the comparison across customers and experimental groups are reliable, we needed to check for demotragphic differences across those groups and the potential effect of the demographic variables on our outcomes. 


# 6. Usage of ControvPay

Before estimating the percentage of users who would use ControvPay as the first option, we first check if there are differences in this regard between users who indicated being customers of the retailer in the last year and those who did not. 

```{r}
# Obtain the frequency table
adoption.customer.table <- with(pay.df, table(adoption, customer))
adoption.customer.table

# Obtain the table of proportions
prop.table(adoption.customer.table, margin = 2)

# Obtain the Chi-Square test
chisq.test (adoption.customer.table)


```

The results suggest that there are not differences between the current retailer' customers and non customers. We therefore calculate the estimation of the use of ControvPay in the whole sample

```{r}
# Calculate the frequency table
adoption.table <- with(pay.df, table(adoption))
adoption.table

# Calculate the proportion table
prop.table(adoption.table)

# Calculate confidence intervals for the adoption rate
adoption.prop <- binom.test (x = adoption.table ["1"],
            n = sum(adoption.table))
adoption.prop

# Prepare the results in a dataframe
adoption.df <- data.frame(
  category = c("not adopted ControvPay", "adopted ControvPay"),
  percentage = as.numeric(prop.table(adoption.table)) * 100,
  lower.ci = NA_real_,
  upper.ci = NA_real_,
  count = as.numeric(adoption.table)
)
adoption.df$lower.ci[adoption.df$category == "adopted ControvPay"] <- adoption.prop$conf.int[1] * 100
adoption.df$upper.ci[adoption.df$category == "adopted ControvPay"] <- adoption.prop$conf.int[2] * 100

adoption.df

```


```{r}

# Plotting the bar graph
ggplot(adoption.df[adoption.df$category == "adopted ControvPay", ], aes(x = category, y = percentage)) +
  
  # Type of graph
  geom_col(width = 0.7, fill = "grey80") +
  
  # Error bars
  geom_errorbar(
    aes(ymin = lower.ci, ymax = upper.ci),
        width = 0.2) +
  
  # Graph title
  labs(
    title = "Adoption of ControvPay",
    y = "% of Customers",
    x = " " ) +
  
  # Data labels
  geom_text(
    aes(y = upper.ci, label = paste0(round(percentage, 0), "%")),         # label with percentage rounded
    position = position_dodge(width = 0.8),   # match the dodge of bars
    vjust = -1,                             # slightly above the bar
    size = 5
  ) +
  
  # Y axis limits para que quepan las etiquetas
  ylim(0, max(adoption.df$upper.ci, na.rm = TRUE) * 1.2) +
  
  # Formatting
  theme_minimal(base_size = 12) +
  theme(plot.title = element_text(hjust = 0.5, face = "bold"), 
           axis.text.x = element_blank() 
  )
  
```





```{r}
###
# Reusable Function to Calculate Percentages and their 95% CI
###

f.prop.dicdvl.1f <- function(my.data, my.dv.list, my.factor){
  
  # Initialize an empty list to store the sampled subsets from each stratum.
  results <- list() 
  
  # Initialize a counter for indexing elements in the 'results' list.
  p <- 1 
  
  # Obtain the levels of the factor
  f.levels <- unique (my.data[[my.factor]])
  
  #Create a loop for each dv and for each level of the factors
    for (dv in my.dv.list){
      for (lf in f.levels){
          
          # Extract the vector, successes and number of cases
          current.vector <- my.data[my.data[[my.factor]]==lf, dv]
          current.vector.c <- as.numeric(current.vector[!is.na(current.vector)]) #cleaning missing cases
          n <- length(current.vector.c) # number of cases in the vector
          s <- length(current.vector.c[current.vector.c == 1]) # number of cases satisfying the condition
          
          # Calculate proportions and their 95% CI
          if(n > 0){
            proportion <- s / n #calculating proportions
            binomial.test <- binom.test (s, n) # binomial test to calculate 95% CI of the proportions
            ci_lower <- binomial.test$conf.int[1] #extracting the lower limit of the CI
            ci_upper <- binomial.test$conf.int[2] #extracting the upper limit of the CI    
          }else{
            proportion <- NA
            ci_lower <- NA
            ci_upper <- NA
          }

          # Save the results in a named vector
          results [[p]] <- data.frame(dep.variable = dv, factor = lf, percentage = proportion * 100, 
                           ci_lower.perc = ci_lower * 100, ci_upper.perc = ci_upper * 100, n.cases = n, stringsAsFactors = FALSE)
          p <- p + 1 
          
      } # close the loop for the factor
    } # close the loop for the dv

  #Combine the results in a dataframe and convert outcomes to numeric columns
  results.df <- (do.call(rbind, results))
  rownames(results.df) <- NULL

  #Return the dataframe
  return(results.df)
}


###
# Application of the function
###

dv.list = c("adoption")

adoption.df <- f.prop.dicdvl.1f (my.data = pay.df,
                  my.dv.list = dv.list,
                  my.factor = "customer")

adoption.df


```



# 6. Checks for Balanced Comparisons


## 6.1. Exploration of demographic effects on Dependent Variables

To identify any relevant effect on the demographic variables on the outcomes, we evaluate the correlations between these two types of variables, which we can observe in the correlation matrix, in a scatterplot matrix or in a correlation plot. 

To gaing a more holistic picture, we include also other variables like condition and customer in the matrix. 

```{r}
# Extract a dataframe with the variables to correlate
cor.df <- pay.df [ , c("age", "gender", "condition", "customer", "social.responsibility", "ease", "purchase.intention", "loyalty")]
cor.df$gender <- as.numeric(ifelse(cor.df$gender == "woman", 0,1))
cor.df$condition <- as.numeric(ifelse(cor.df$condition == "control", 0,1))
cor.df$customer <- as.numeric(ifelse(cor.df$customer == "no", 0,1))


# Correlation matrix 
corr.test (cor.df, use = "complete.obs")

# Scatterplot matrix
scatterplotMatrix (cor.df, use = "complete.obs")

# Correlation plot
corrplot.mixed(corr = cor(cor.df, use = "complete.obs"), upper = "ellipse")
```

Correlation analysis revealed that age was significantly associated with ease of use, purchase intention, and loyalty. In contrast, gender showed very weak correlations with any outcome variables (all p > .05). Let's further explore if age and gender are different across the experimental assignment condition and across type of customers, to see if their effects can contaminate the results. 


## 6.1. Balance in Experimental Assignment

We assessed whether the control and experimental groups differed on age, gender, or customer status using descriptive statistics, visualizations, and statistical tests (chi-square tests for categorical variables, independent t-tests for age).

```{r}

# Obtain general descriptives by experimental condition
describeBy(pay.df[, c("age", "gender", "customer")], group = pay.df$condition)

# Check for statistical differences in age with an independent samples t-test
t.test(age ~ condition, data = pay.df)
cohens_d(age ~ condition, data = pay.df)

# Check for statistical differences in gender with a chi square test
table.gender.condition <- with (pay.df, table(gender,condition))
chisq.test(table.gender.condition)

# Check for statistical differences in customers ratio with a chi-square test
table.customer.condition <- with (pay.df, table(customer,condition))
chisq.test(table.customer.condition)


# Obtain visualizations

par(mfrow = c(1, 3))
boxplot(age ~ condition, data = pay.df, main = "Age by Condition")
barplot(table.gender.condition, beside = TRUE, main = "Gender Distribution")
barplot(table.customer.condition, beside = TRUE, main = "Customer Distribution")
par(mfrow = c(1, 1))

```

The two experimental gropus are similar in terms of age, gender, and customers ratio. Yet, since we are also considering being a customer as a potential interaction factor, we also check the assignment balance within customers and non customer.


## 6.2. Balance in Customers Groups

We assessed whether the customer groups within the control and experimental groups differed on age and gender using descriptive statistics, visualizations, and statistical tests (chi-square test for gender, factorial ANOVA test for age).

```{r}

# Obtain general descriptives by condition and customer groups
describeBy(pay.df[, c("age", "gender")], group = list(pay.df$condition, pay.df$customer))

# Factorial ANOVA for testing differences across age
age_anova <- aov(age ~ condition * customer, data = pay.df)
summary(age_anova)
age.eta.squared <- eta_squared(age_anova, partial = TRUE) 
age.eta.squared

# Chi-square for genders  
# We first create a variable grouping participants by both experimental group and customer group
pay.df$condition.customer <- rep(NA_character_, nrow(pay.df))
pay.df$condition.customer [pay.df$condition == "experimental" & pay.df$customer == "yes"] <- "exp.customers"
pay.df$condition.customer [pay.df$condition == "experimental" & pay.df$customer == "no"] <- "exp.non.customers"
pay.df$condition.customer [pay.df$condition == "control" & pay.df$customer == "yes"] <- "ct.customers"
pay.df$condition.customer [pay.df$condition == "control" & pay.df$customer == "no"] <- "ct.non.customers"
pay.df$condition.customer <- factor(pay.df$condition.customer)


# Chi-square
table.gender.condition.customer <- with (pay.df, table(gender, condition.customer))
chisq.test(table.gender.condition.customer)


# Visualization for the four groups

# Set more margins in the bottom
par(mar = c(8, 4.1, 4.1, 2.1)) 

# Age by 2x2 groups
boxplot(age ~ condition.customer, data = pay.df,
        main = "Age Distribution by Condition × Customer",
        las = 2) # Rotate x-axis labels



# Gender proportions by 2x2 groups
barplot(table.gender.condition.customer, beside = TRUE,
        main = "Gender by Condition × Customer",
        legend.text = TRUE)

par(mar = c(5.1, 4.1, 4.1, 2.1)) 

```

The factorial ANOVA revealed no significant interaction between condition and customer status for age (F(1, 796) = X.XX, p = .XXX), and the chi-square test showed no significant association between the combined condition-customer groups and gender distribution (χ²(3) = X.XX, p = .XXX). This indicates successful balance across all four experimental cells, supporting the internal validity of subsequent comparisons

Attending to the scarce differences in age and gender across our experimental variables, we proceed with the following analyses without considering them as covariates.




# 7. Experimental Effects Analysis

To evaluate the causal impact of exposing participants to ControvPay versus traditional payment methods only, we used several 2×2 factorial Analysis of Variance (ANOVA). This design allowed us to test both the main effect of the experimental condition and its potential interaction with participants' customer status (current customers vs. non-customers of the retailer). 

Specifically, the analysis addresses three key questions:

* 1. Does the presence of ControvPay influence consumer perceptions and intentions?
* 2. Do these effects differ between existing customers and non-customers?


We started by checking the normality assumption for conducting ANOVA testS. 


## 7.1. Checking the Normality Assumption

To evaluate the normality assumption, we conducted histograms, normal Q-Q plots, and indexes of skewness and kurtosis. 

```{r}

# Skewness and kurtosis

normality.indexes.df <- describe (pay.df[ , c("social.responsibility", "ease", "purchase.intention", "loyalty")])
normality.indexes.df <- normality.indexes.df [ , c("skew", "kurtosis")]
normality.indexes.df 

# Prepare the output for 4 plots
par(mfrow = c(2, 2))

# Histograms
hist(pay.df$social.responsibility)
hist(pay.df$ease)
hist(pay.df$purchase.intention)
hist(pay.df$loyalty)


# QQ plots

# Social responsibility
qqnorm(pay.df$social.responsibility, main = "social responsibility")
qqline(pay.df$social.responsibility)

# Ease of use
qqnorm(pay.df$ease, main = "ease of use")
qqline(pay.df$ease)

# Purchase intention
qqnorm(pay.df$purchase.intention, main = "purchase intention")
qqline(pay.df$purchase.intention)

# Loyalty
qqnorm(pay.df$loyalty, main = "loyalty")
qqline(pay.df$loyalty)

```

The distributions of purchase intentions and loyalty approximate closely to their theoretical normal distributions. The histogram for social responsibility and ease of use perceptions suggest respectively  ceiling and bottom effects, leading to skewness. Yet, this level of skewness appears to be tolerable, as indicated by skewness indexes within the +/- 1 range, and QQplots where the distribution approximates to the theoretical normal distribution. We then proceed with the ANOVA models for all variables, as ANOVA is robust to moderate levels of normality deviations in large samples.  


## 7.2. Factorial Anova Models

To perform the comparison across conditionos, we used a 2 (condition: experimental versus control) x 2 (retailer customer: customer versus non customer) factorial ANOVA for each of our dependent variables. For that, we used a reusable function from my Tookit, expecified below. 


```{r}

f.factorial.anova <- function (my.data, my.dv.list, my.factor1, my.factor2) {
  
  # Initiate lists to save different type of results
  anova.results <- list() # to keep ANOVA results
  a <- 1
  descriptive.results <- list() # to keep descriptives
  d <- 1
  cohen.d.results <- list() # to keep cohen d results
  c <- 1
  tukey.results <- list() # to keep Tukey results
  t <- 1
  
  # Obtain the levels of the factors
  f1.levels <- unique (my.data[[my.factor1]])
  f2.levels <- unique (my.data[[my.factor2]])
  
  # Specify function for Cohen d calculation
    f.cohen.d.calculation <- function (groups.data, groups.matrix, dv.name, effect.name, level.names) {
    
      # Create a list to store the results
      fd.results.list <- list()
      fd <- 1 # index for the above list
    
      # Open a loop for each comparison
      for (i.comparison in 1:nrow(groups.matrix)){
      
        # Obtain the group indexes to compare
        index.g1 <- groups.matrix [i.comparison, 1]
        index.g2 <- groups.matrix [i.comparison, 2]
      
        # Obtain the names of groups compared
        name.g1 <- groups.data [index.g1, level.names]
        name.g2 <- groups.data [index.g2, level.names]
      
        # Obtain the means of groups compared
        mean.g1 <- groups.data [index.g1, "mean"]
        mean.g2 <- groups.data [index.g2, "mean"]
      
        # Obtain the sd of groups compared
        sd.g1 <- groups.data [index.g1, "sd"]
        sd.g2 <- groups.data [index.g2, "sd"]
      
        # Obtain the n of groups compared
        n.g1 <- groups.data [index.g1, "n"]
        n.g2 <- groups.data [index.g2, "n"]     
      
        # Calculate the pooled standard deviation
        pooled.sd <- sqrt(((n.g1 - 1) * sd.g1^2 + (n.g2 - 1) * sd.g2^2) / (n.g1 + n.g2 - 2))
      
        # Calculate Cohen's d
        cohen.d <- (mean.g1 - mean.g2)/ pooled.sd
      
        # Save the results for each comparison
        comparison.cohen.d.result <- data.frame (
          dep.variable = dv.name,
          effect = effect.name,
          group1 = name.g1,
          group2 = name.g2,
          d = cohen.d, 
          sd.pooled = pooled.sd
        )
        fd.results.list [[fd]] <- comparison.cohen.d.result
        fd <- fd + 1
      
      } # Close the loop within the f.cohen.d.calculation   
      
      d.function.results <- do.call(rbind, fd.results.list)
      
    # Return the result for the effect
    return (d.function.results)
   
    } # Close the f.cohen.d.calculation function
      
 
     
  # Initiate a loop for each dv
  for (dv in my.dv.list) {
    
    
#--- 1. Metrics for the ANOVA models
    
    # Build a dynamic formula
    anova.formula <- as.formula (paste0(dv, "~", my.factor1, "*", my.factor2))

    # Fit the ANOVA model
    anova.model <- aov(anova.formula, data = my.data)
    
    # Extract the model in a dataframe
    anova.table <- anova(anova.model)
    
    # Bind the anova table with a dataframe that contains the dv names
    anova.result.df <- data.frame (dep.variable = rep(dv, nrow(anova.table)), 
                                    effect = rownames(anova.table))
    anova.result.df <- bind_cols (anova.result.df, anova.table)
    
    # Add the eta squared (Proportional Reduction in Error)
    ss.total <- sum(anova.table[ , "Sum Sq"]) # sum of error
    anova.result.df$eta.squared <- anova.result.df[["Sum Sq"]] / ss.total
    
    # Save the results
    anova.results [[a]] <- anova.result.df
    a <- a + 1
    
 
    
#--- 2. Posthoc Comparison with Tukey
    
    # Obtain the Tukey results
    tukey <- TukeyHSD(anova.model)
    
    # Bind the comparisons for main effects and interaction effects in a single dataframe
    for (name.effect in names(tukey)) {
      
      # Extract the comparisons for the effect
      tukey.df <- as.data.frame(tukey[[name.effect]])
      tukey.df$dep.variable <- dv
      tukey.df$effect <- name.effect
      tukey.df$comparison <- rownames(tukey.df)
      tukey.results [[t]] <- tukey.df
      t <- t + 1
    } # Close the loop for the Tukey effect       
    
    
    
#--- 3. Descriptive Statistics
    
    # -- 3.1. Descriptives for factor 1
    
    # Open a loop for factor 1
    for (f1.level in f1.levels){
      
      # Create a vector with the scores of each level in factor 1
      current.vector <- my.data[my.data[[my.factor1]] == f1.level , dv]
      
      # Clean missind data
      current.vector.c <- current.vector[!is.na(current.vector)]
      
      # Obtain the mean, standard deviations, standard errors, n, and 95% CI
      mean.level <- mean(current.vector.c)
      sd.level <- sd(current.vector.c)
      n.level <- length(current.vector.c)
      se.level <- sd.level / sqrt(n.level)
      upper.ci.level <- mean.level + 1.96 * se.level
      lower.ci.level <- mean.level - 1.96 * se.level
      
      # Save the results
      level.descriptive.results <- data.frame (
        dep.variable = dv, 
        factor1.levels = f1.level,
        factor2.levels = paste0 ("all"),
        mean = mean.level,
        sd = sd.level,
        upper.ci = upper.ci.level,
        lower.ci = lower.ci.level,
        se = se.level,
        n = n.level, 
        level.name = f1.level)
      
      
      descriptive.results[[d]] <- level.descriptive.results
      d <- d + 1
    
    } # Close the loop for factor 1
     
    
    # -- 3.2. Descriptives for factor 2
      
    # Open a loop for factor 2
    for (f2.level in f2.levels){
      
      # Create a vector with the scores of each level in factor 2
      current.vector <- my.data[my.data[[my.factor2]] == f2.level , dv]
      
      # Clean missind data
      current.vector.c <- current.vector[!is.na(current.vector)]
      
      # Obtain the mean, standard deviations, standard errors, n, and 95% CI
      mean.level <- mean(current.vector.c)
      sd.level <- sd(current.vector.c)
      n.level <- length(current.vector.c)
      se.level <- sd.level / sqrt(n.level)
      upper.ci.level <- mean.level + 1.96 * se.level
      lower.ci.level <- mean.level - 1.96 * se.level
      
      # Save the results
      level.descriptive.results <- data.frame (
        dep.variable = dv, 
        factor1.levels = paste0 ("all"),
        factor2.levels = f2.level,
        mean = mean.level,
        sd = sd.level,
        upper.ci = upper.ci.level,
        lower.ci = lower.ci.level,
        se = se.level,
        n = n.level,
        level.name = f2.level
      )
      
      descriptive.results[[d]] <- level.descriptive.results
      d <- d + 1
      
      } # Close the loop for factor 2
    
    
    # -- 3.3. Descriptives for the interaction
    
      # Open loops for the interaction

      for (f1.level in f1.levels){
        for (f2.level in f2.levels){
      
        # Create a vector with the scores of the interaction level
        current.vector <- my.data [my.data[[my.factor1]] == f1.level &  my.data[[my.factor2]] == f2.level, dv ]
      
        # Clean missind data
        current.vector.c <- current.vector[!is.na(current.vector)]
      
        # Obtain the mean, standard deviations, standard errors, n, and 95% CI
        mean.level <- mean(current.vector.c)
        sd.level <- sd(current.vector.c)
        n.level <- length(current.vector.c)
        se.level <- sd.level / sqrt(n.level)
        upper.ci.level <- mean.level + 1.96 * se.level
        lower.ci.level <- mean.level - 1.96 * se.level
      
        # Save the results
        level.descriptive.results <- data.frame (
        dep.variable = dv, 
        factor1.levels = f1.level,
        factor2.levels = f2.level,
        mean = mean.level,
        sd = sd.level,
        upper.ci = upper.ci.level,
        lower.ci = lower.ci.level,
        se = se.level,
        n = n.level,
        level.name = paste0(f1.level, ":", f2.level)
      )
      
      descriptive.results[[d]] <- level.descriptive.results
      d <- d + 1
    
    } # Close the loop of factor 1 in the interaction loops
      }  # Close the loop of factor 2 in the interaction loop
    
    
# --- 4. Cohen's d Calculations
    
    # -- 4.1. Cohen's d for factor 1 comparisons
    
    # Extract the descriptives for factor 1
    data.groups.to.compare <- do.call(rbind, descriptive.results)
    data.groups.to.compare <- data.groups.to.compare[data.groups.to.compare$dep.variable == dv & 
                                   data.groups.to.compare$factor2.levels == "all", ]
    
    # Obtain the number of groups
    n.groups <- nrow(data.groups.to.compare)
    
    # Obtain a matrix with the group combination indexes
    comparison.matrix <- as.data.frame(t(combn(1:n.groups, 2)))
    
    # Apply the f.cohen.d.calculation function to calculate the d results for factor 1
    factor1.d.results <- f.cohen.d.calculation(
      groups.data = data.groups.to.compare,
      groups.matrix = comparison.matrix,
      dv.name = dv,
      effect.name = my.factor1, 
      level.names = "level.name"
    )
    
    # Save the d results for the factor 1  groups
    cohen.d.results[[c]] <- factor1.d.results
    c <- c + 1
    
    
    # -- 4.2. Cohen's d for factor 2 comparisons
    
    # Extract the descriptives for factor 2
    data.groups.to.compare <- do.call(rbind, descriptive.results)
    data.groups.to.compare <- data.groups.to.compare[data.groups.to.compare$dep.variable == dv & 
                                   data.groups.to.compare$factor1.levels == "all", ]
    
    # Obtain the number of groups
    n.groups <- nrow(data.groups.to.compare)
    
    # Obtain a matrix with the group combination indexes
    comparison.matrix <- as.data.frame(t(combn(1:n.groups, 2)))
    
    # Apply the f.cohen.d.calculation function to calculate the d results for factor 2
    factor2.d.results <- f.cohen.d.calculation(
      groups.data = data.groups.to.compare,
      groups.matrix = comparison.matrix,
      dv.name = dv,
      effect.name = my.factor2,
      level.names = "level.name"
    )    
    
    # Save the d results for the factor 2  groups
    cohen.d.results[[c]] <- factor2.d.results
    c <- c + 1  
    

    # -- 4.3. Cohen's d for the interaction comparisons
    
    # Extract the descriptives for the interaction
    data.groups.to.compare <- do.call(rbind, descriptive.results)
    data.groups.to.compare <- data.groups.to.compare[data.groups.to.compare$dep.variable == dv & 
                                  data.groups.to.compare$factor1.levels != "all" &
                                  data.groups.to.compare$factor2.levels != "all", 
                                  ]
    
    # Obtain the number of groups
    n.groups <- nrow(data.groups.to.compare)
    
    # Obtain a matrix with the group combination indexes
    comparison.matrix <- as.data.frame(t(combn(1:n.groups, 2)))
    
    # Apply the f.cohen.d.calculation function to calculate the d results for the interaction
    interaction.d.results <- f.cohen.d.calculation(
      groups.data = data.groups.to.compare,
      groups.matrix = comparison.matrix,
      dv.name = dv,
      effect.name = paste0(my.factor1, ":", my.factor2),
      level.names = "level.name"
    )    
    
    # Save the d results for the factor 2  groups
    cohen.d.results[[c]] <- interaction.d.results
    c <- c + 1  
    

    
} # close the dv loop
  

    
#--- 5. Save all the results

  
  #--- ANOVA Results
  
  # Group the anova results in a dataframe
  anova.results.df <- do.call(rbind, anova.results)
  rownames(anova.results.df) <- NULL
  
  # Round the data columns
  numeric.cols <- sapply(anova.results.df, is.numeric)
  anova.results.df[numeric.cols] <- round(anova.results.df[numeric.cols], 3)
  
  
  #--- Descriptive Results
  
  # Group the descriptives for all levels
  descriptives.df <- do.call(rbind, descriptive.results)
  
  # Round the columns
  numeric.cols <- sapply(descriptives.df, is.numeric)
  descriptives.df[numeric.cols] <- round(descriptives.df[numeric.cols], 2)
  
  # Rename the factor columns
  names (descriptives.df)[names(descriptives.df) == "factor1.levels"] <- my.factor1
  names (descriptives.df)[names(descriptives.df) == "factor2.levels"] <- my.factor2
  
  
  #--- Cohen's d Results
  
  # Group the d results for all comparisons
  cohen.d.df <- do.call(rbind, cohen.d.results)
  
  # Add a "comparison" variable" to use as a key for the Tukey results, duplicating all comparisons with the altered order
  cohen.d.df1 <- cohen.d.df
  cohen.d.df1$comparison <- paste0 (cohen.d.df1$group1, "-", cohen.d.df1$group2)
  cohen.d.df2 <- cohen.d.df
  cohen.d.df2$comparison <- paste0 (cohen.d.df2$group2, "-", cohen.d.df2$group1)
  cohen.d.df2$d <- cohen.d.df2$d *(-1)
  doubled.cohen.d.df <- bind_rows(cohen.d.df1, cohen.d.df2)
  
  
  #--- Tukey Results
  
  # Group all the Tukey results
  tukey.results.df <- do.call(rbind, tukey.results)
  rownames(tukey.results.df) <- NULL
  
  # Reorder the columns
  index.tukey <- tukey.results.df [ , c("dep.variable", "effect", "comparison")]
  tukey.results.df[ , c("dep.variable", "effect", "comparison")] <- NULL
  tukey.results.df <- bind_cols(index.tukey, tukey.results.df)
  
  # Add the Cohen's d results
  tukey.results.df <- merge(tukey.results.df, doubled.cohen.d.df, by = c("dep.variable", "effect", "comparison"), all.x = TRUE)
  tukey.results.df$group1 <- NULL
  tukey.results.df$group2 <- NULL

  #--- List with all the results
  
  results <- list(anova = anova.results.df, 
                  descriptives = descriptives.df,
                  cohen.d = cohen.d.df,
                  tukey = tukey.results.df)
  
  # Return the results
  return(results)

}


```


Now we can apply the function to our data. 


```{r}

dv.variables <- c("social.responsibility", "ease", "purchase.intention", "loyalty")

pay.results <- f.factorial.anova (
  my.data = pay.df,
  my.dv.list = dv.variables,
  my.factor1 = "condition",
  my.factor2 = "customer"
)


pay.anova.df <- pay.results$anova
pay.anova.df

pay.descriptives.df <- pay.results$descriptives
pay.descriptives.df

pay.tukey.df <- pay.results$tukey
pay.tukey.df


```


Although we do not find any significant difference at the level p < 0.5, the interaction between the experimental condition and being customer was significant for the social responsibility perception, with those who were customers of the retailer having a lower perception of responsibility when exposed to the ControvPay option than those not exposed to it (d = -.27, Tukey p = .04). 

For other dependent variables, all differences were far from being statistically significant, but at the descriptive level we can find that the results of loyalty follow a similar pattern than the one found for social responsibility, in which the retailers customers have lower loyalty when exposed to the ControvPay option than those not exposed to it (d = -0.12, Tukey p = .594). 

We can better see these interaction effects in bar graphs: 


```{r}

# Select the descriptives of the interaction to graph
pay.descriptives.int.df <- pay.descriptives.df [!(pay.descriptives.df$condition == "all") & !(pay.descriptives.df$customer =="all"), ]


# Titles for each faceted graph representing a type of complaint
custom_titles <- c(
  social.responsibility   = "Soc. responsibility Perception",
  ease     = "Ease Perception",
  purchase.intention = "Purchase Intention",
  loyalty   = "Loyalty"
)

# Plotting the bar graph
ggplot(pay.descriptives.int.df, aes(x = condition, y = mean, fill = customer)) + # specify variables
  
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +  # specify bar graph
  
  geom_errorbar(
    aes(ymin = lower.ci, ymax = upper.ci),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) + # error bars
  
  facet_wrap(~ dep.variable, 
             scales = "fixed", 
             axes = "all", #
             labeller = labeller(dep.variable = custom_titles)) + # specify facets for each dv
  labs(
    y = "Mean Scores",
    x = "Experimental Condition",
    fill = "Customer",
    title = "Differences Across Experimental Conditions"
  ) + # labels
  
  scale_x_discrete(labels = c ("No ControvPay", "ControvPay")) + # x labels
  
  geom_text(
    aes(y = upper.ci, label = paste0(round(mean, 2))), # use upper ci as reference position
    position = position_dodge(width = 0.8),   # match the dodge of bars
    vjust = -0.5,                             # slightly above the bar
    size = 2.5                                # text size
  ) + # data labels
  
  coord_cartesian(ylim = c(3, 6.2)) +  # limits of the graph
  
  theme_minimal(base_size = 12) +
  
  theme(
    axis.title.x = element_blank(),
    legend.position = "right",
    legend.justification = c("right", "bottom"),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text  = element_text(size = 10),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    strip.text = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, vjust = 0, hjust = 0.5),  
    plot.margin = margin(10, 5, 10, 5)
  ) # Margins and position of elements

```


In the graph we can see that the difference in social responsibility perception and loyalty for customers who experienced ControvPay are very small, just mildly lower than other participants. Yet, it is important to further evaluate the significance of these differences because they refer to possibilities of losing customers in case the company introduced the new payment method. We proceeded with Bayesian analyses to further evaluate this significance, and as a sensitivity complementation to our ANOVA analyses.  



## Bayesian Sensitivity Analysis

To conduct Bayesian Anova for the perception of social responsibility and loyalty, we use a function from my Toolkit.

To be able to have sensitivity in the evaluation of small effects, we use r = 0.1 as one of our priors. 

```{r}

f.bayes.anova <- function (my.data, my.dv.list, my.factor.list, my.priors){
  
  # Empty list to store the results
  bayes.results <- list()  
  
  # Empty list to store a summary of the results
  summary.bayes.results <- list()
  p <- 1
  
  # Create a formula for the factors
  factor.formula = paste0 ("~ ")
    for (i.factor in seq_along(my.factor.list)){
      if (i.factor != length(my.factor.list)) {
           factor.formula <-  paste0 (factor.formula, my.factor.list[i.factor], " * ")      
      } # Close if formula
           else {
             factor.formula <-  paste0 (factor.formula, my.factor.list[i.factor])
           }
  } # Close the loop for the factors
  
  
  # Loop for each dependent variable
  for (dv in my.dv.list) {
    
    for(prior in my.priors) {
      
      bayes.model <- anovaBF(as.formula(paste(dv, factor.formula)),
                      data = my.data,
                      rscaleFixed = prior,  
                      whichModels = 'all'
      )
      
      # Dynamic name for the model
      model.name <- paste0  (dv, ".prior.", prior)
      
      # Save the results for each model
      bayes.results[[model.name]] <- bayes.model
      
      # Create a dataframe for the results summary
      model.df <- as.data.frame (bayes.model)
      model.df$dep.variable <- paste0 (dv)
      model.df$prior <- paste0 (prior)
      model.df$effect <- row.names(model.df)
      model.df$BF010 <- model.df[[1]]
      model.df$error <- model.df[[2]]
      model.df <- model.df [ , c("dep.variable", "prior", "effect", "BF010", "error")]
      
      # Save the results summary dataframe in the list
      summary.bayes.results [[p]] <- model.df
      p <- p  + 1 
      
    } # Close the loop for the priors
    
  } # Close the loop for the DVs
  
  # Unify the summary results for all dvs and priors
  summary.df <- do.call(rbind, summary.bayes.results)
  row.names(summary.df) <- NULL
  bayes.results[["summary"]] <- summary.df
  
  
  return(bayes.results)
  
}

```

Application of the formula


```{r}

# Specify the priors
priors <- c(0.1, 0.5, 1)  # Vector con los dos tipos de "priors" que vamos a probar


# Specifiy the DV list
dvs <- c("social.responsibility", "loyalty")

# Specify the factors
factors <- c("condition", "customer")

# Apply the function
bayes.anova.results <- f.bayes.anova (my.data = pay.df, my.dv.list = dvs, my.factor.list = factors, my.priors = priors)


# Print the summary of the results
summary.bayes <- bayes.anova.results [["summary"]]
summary.bayes

```

For **loyalty**, the evidence consistently supported the absence of an interaction effect across all priors. While this conclusion is currently only supported by anecdotal to moderate evidence, it suggests that ControvPay is unlikely to substantially impact customer loyalty. 

For **social responsibility**, the results present ambiguous evidence regarding an interaction effect. With more conservative priors (rscale = 0.5 or 1.0), the evidence favored the null hypothesis of no differential effect between experimental conditions across customer profiles. However, these priors are less sensitive to detecting small effects. Conversely, when using a more sensitive prior (rscale = 0.1), we found anecdotal evidence for an interaction effect, though such sensitive priors also increase the risk of detecting statistical noise.

Given that even small decreases in social responsibility perceptions could be impactful for our large-scale retailer, we proceeded to quantify this potential effect using Monte Carlo simulation chains to estimate the practical significance of this ambiguous finding.

```{r}

# Extract the model for social responsibility
m.soc.resp.0.1 <- bayes.anova.results[["social.responsibility.prior.0.1"]]

# Simulate the Monte Carlo chains
chain.bayes.social.responsibility <- posterior(m.soc.resp.0.1, 
                                               index = 7, 
                                               iterations = 10000)

# Convergence diagnostics of Monte Carlo chains
plot(chain.bayes.social.responsibility [, 1:10])

# Inspect the Monte Carlo chains
summary(chain.bayes.social.responsibility)


###
# Obtain mean estimations and 95% credible intervals
###

# Calculate the distributions for the main effects
d.main.effects <- data.frame(chain.bayes.social.responsibility[ , 2:5] + chain.bayes.social.responsibility[ , 1])

# Calculate the distributions for the interaction effects
d.control.yes <- chain.bayes.social.responsibility[ , "mu"] + 
            chain.bayes.social.responsibility[ , "condition-control"] +
            chain.bayes.social.responsibility[ , "customer-yes"] + 
            chain.bayes.social.responsibility[ , "condition:customer-control.&.yes"]

d.control.no <- chain.bayes.social.responsibility[ , "mu"] + 
            chain.bayes.social.responsibility[ , "condition-control"] +
            chain.bayes.social.responsibility[ , "customer-no"] + 
            chain.bayes.social.responsibility[ , "condition:customer-control.&.no"]

d.experimental.yes <- chain.bayes.social.responsibility[ , "mu"] + 
            chain.bayes.social.responsibility[ , "condition-experimental"] +
            chain.bayes.social.responsibility[ , "customer-yes"] + 
            chain.bayes.social.responsibility[ , "condition:customer-experimental.&.yes"]

d.experimental.no <- chain.bayes.social.responsibility[ , "mu"] + 
            chain.bayes.social.responsibility[ , "condition-experimental"] +
            chain.bayes.social.responsibility[ , "customer-no"] + 
            chain.bayes.social.responsibility[ , "condition:customer-experimental.&.no"]

# Group the results
estimations <- bind_cols(as.data.frame(d.main.effects), 
                         condition.control_customer.yes = d.control.yes, 
                         condition.control_customer.no = d.control.no, 
                         condition.experimental_customer.yes = d.experimental.yes, 
                         condition.experimental.customer.no = d.experimental.no)


# Calculate 95% credible intervals
credible.intervals.soc.resp <- t(apply(estimations, 2, quantile, pr = c(0.025, 0.5, 0.975)))

# Save the credible intervals in a dataframe
credible.intervals.soc.resp.df <- data.frame(
  group = rownames(credible.intervals.soc.resp),
  median = credible.intervals.soc.resp[, "50%"],
  lower.ci = credible.intervals.soc.resp[, "2.5%"],
  upper.ci = credible.intervals.soc.resp[, "97.5%"]
)


row.names (credible.intervals.soc.resp.df) <- NULL

credible.intervals.soc.resp.df


```

The convergence diagnostics indicate that the model estimations were stable and converged appropriately (homogeneous patterns in the trace plots and normal distributions of the simulation results). The estimated means and credible intervals are coherent with the descriptive data. For better interpretation, we visualize them below.



```{r}
# Gráfico más informativo
ggplot(credible.intervals.soc.resp.df, aes(x = group, y = median)) +
  geom_pointrange(aes(ymin = lower.ci, ymax = upper.ci), 
                  size = 0.7, color = "black") +
  geom_point(size = 2, color = "black") +
  labs(title = "Posterior Distributions - Social Responsibility Perception",
       subtitle = "Points show median estimates, bars show 95% credible intervals",
       y = "Social Responsibility Score (1-7 scale)", 
       x = "Experimental Group") +
  theme_bw() +
  coord_flip() +
  theme(plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(color = "gray40"))
```

The posterior distributions reveal a clear interaction pattern: ControvPay differentially affects existing customers versus non-customers:

- Existing customers: Decrease of 0.21 points [95% CI: 0.14, 0.29] in social responsibility perception

- Non-customers: Negligible change (0.01 points difference)

Business Implications:

The potential negative impact is concentrated among the retailer's existing customer base, suggesting that brand loyalty may create higher expectations for ethical business practices. While the effect size is small, it could be meaningful given the large customer base.

This pattern aligns with the ambiguous but suggestive evidence from the Bayesian ANOVA, providing concrete estimates of the potential effect magnitude.

To further investigate this difference, we specifically evaluate the contrast between experimental conditions within the customer group using Bayesian post-hoc comparisons.


```{r}

# Calculate the estimated distribution of differences between experimental conditions within customers
dif.in.customers <- d.control.yes - d.experimental.yes

# Calculaate mean and credible intervals for the difference
ci.dif.in.customers <- quantile(dif.in.customers, pr = c(0.025, 0.5, 0.975))
ci.dif.in.customers

```

The results confirm that the perception of social responsibility is significantly lower for the retailer's customers who were exposed to the ControvPay option compared to those not exposed to it [median difference = 0.21 points, 95% CI: 0.03, 0.41].

The emergence of this difference specifically among existing customers aligns with theoretical expectations, as the retailer is known for high ethical standards, and its customers are likely more sensitive to ethical controversies in payment methods.

To further explore the downstream consequences of this difference on impactful outcomes like customer loyalty and purchase intention, we conduct mediation analyses within the customer subgroup.


# Path Analyses

Although prior analyses indicated no significant direct differences in loyalty and purchase intention between experimental conditions, it is possible that these effects were small and masked by statistical noise. This suspicion is supported by the difference we found in social responsibility perception among the retailer's customers, combined with our knowledge that loyalty and purchase intention are related to social responsibility perceptions (see correlation analyses in Section X).

A mediation analysis examining the experimental effect through social responsibility perceptions can help identify these potential indirect pathways.

## Checking the Fit of Path Analyses Models

We know collinearity between experimental conditions and social responsibility perception is not problematic for predicting other variables, as they are only slightly related (d < .30) (see Section X).

To identify potential issues with outliers, normality, linearity, homoscedasticity, and independence of residuals, we will:

* Specify the linear regression models implied in the path analysis.
* Plot the distribution of residuals and identify outliers' influence on model estimates

```{r}

# Select subsample of retailer's customers
customers.pay.df <- pay.df[pay.df$customer == "yes", ]

# Model the two steps of path analysis for both DVs with multiple regression
m.path.1 <- lm(social.responsibility ~ condition, data = customers.pay.df)
m.path.2.loyalty <- lm(loyalty ~ condition + social.responsibility, data = customers.pay.df)
m.path.2.purchase.intention <- lm(purchase.intention ~ condition + social.responsibility, data = customers.pay.df)

# Obtain diagnostic plots
par(mfrow =c(2,2)) #To set the graph objects to a 2x2 format
plot(m.path.1)
plot(m.path.2.loyalty) 
plot(m.path.2.purchase.intention)

```

In the residual vs. fitted values plots, we observe a homogeneous pattern across fitted values, suggesting linear relationships and absence of heteroscedasticity issues.

The normal Q-Q plots indicate that standardized residuals closely follow the theoretical normal distribution, suggesting no major normality violations.

The residual vs. leverage plots identify some potentially influential outliers based on high standardized residuals and leverage (cases 606, 786, 179, 294, 310, 23, 557, and 134). We will inspect these cases to identify potential data quality issues.

```{r}

customers.pay.df[customers.pay.df$id %in% c(606, 786, 179, 294, 310, 23, 557, 134), ]

```


We did not observe major data problems. Although we observed some extreme scores in either purchase intention or loyalty, these scores tended to be in line with other important variables like the perception of ease. 

We therefore maintain the analyses with all cases to avoid artificial data manipulations.


## Path Modeling Purchase Intention

To analyze the mediation effect of the experimental condition on purchase intention through the perception of social responsibility, we use the R extension PROCESS (https://www.processmacro.org/index.html).

```{r}
# Convert condition to numeric for PROCESS
customers.pay.df$condition_num <- ifelse(customers.pay.df$condition == "experimental", 1, 0)

# Run mediation analysis
process(data = customers.pay.df, 
        y = "purchase.intention", 
        x = "condition_num", 
        m = "social.responsibility", 
        model = 4, 
        boot = 5000,
        seed = 123)

```

To better interpret the results, we represent them in a path diagram



```{r}

# Create diagram with DOT notation
grViz("
digraph mediation {
  graph [layout = neato, overlap = false, fontname = Arial]
  
  node [shape = rectangle, style = filled, fillcolor = 'lightblue', fontname = Arial]
  
  Condition [pos = '0,1!', label = 'Adding ControvPay']
  SocialResponsibility [pos = '2,2!', label = 'Social Responsibility\\nPerception']
  PurchaseIntention [pos = '4,1!', label = 'Purchase Intention']
  
  // Direct Effects
  Condition -> SocialResponsibility [label = 'a = -0.28*', fontsize = 12, color = 'black']
  SocialResponsibility -> PurchaseIntention [label = 'b = 0.09 (ns)', fontsize = 12, color = 'grey', style = 'dashed']
  Condition -> PurchaseIntention [label = 'c = 0.00 (ns)', fontsize = 12, color = 'grey', style = 'dashed']
  
  // Indirect Effect
  Indirect [shape = plaintext, pos = '2,0!', fillcolor = 'none']
  Indirect [label = 'Indirect Effect: a×b = -0.02\\n[95% CI: -0.07, 0.01]', fontsize = 14, color = 'darkred']
}
")

```

The path analysis indicates that social responsibility perceptions do not significantly mediate the relationship between ControvPay exposure and purchase intention. The indirect effect is negligible (effect = -0.02) and the 95% confidence interval includes zero [-0.07, 0.01], indicating statistical non-significance.

This suggests that while social responsibility perceptions affect loyalty, they do not translate into significant changes in immediate purchase intentions among existing customers.


## Path Modeling for Loyalty

To analyze the mediation effect of the experimental condition on loyalty through the perception of social responsibility, we use the R extension PROCESS (https://www.processmacro.org/index.html).

```{r}



# Run mediation analysis
process(data = customers.pay.df, 
        y = "loyalty", 
        x = "condition_num", 
        m = "social.responsibility", 
        model = 4, 
        boot = 5000,
        seed = 123)

```

To better visualize the results from this output, we represent them in a path diagram.

```{r}

# Create diagram with DOT notation
grViz("
digraph mediation {
  graph [layout = neato, overlap = false, fontname = Arial]
  
  node [shape = rectangle, style = filled, fillcolor = 'lightblue', fontname = Arial]
  
  Condition [pos = '0,1!', label = 'Adding ControvPay']
  SocialResponsibility [pos = '2,2!', label = 'Social Responsibility\\nPerception']
  Loyalty [pos = '4,1!', label = 'Loyalty']
  
  // Direct Effects
  Condition -> SocialResponsibility [label = 'a = -0.28*', fontsize = 12, color = 'black']
  SocialResponsibility -> Loyalty [label = 'b = 0.54 ***', fontsize = 12, color = 'black']
  Condition -> Loyalty [label = 'c = -0.03 (ns)', fontsize = 12, color = 'grey', style = 'dashed']
  
  // Indirect Effect
  Indirect [shape = plaintext, pos = '2,0!', fillcolor = 'none']
  Indirect [label = 'Indirect Effect: a×b = -0.15*\\n[95% CI: -0.27, -0.04]', fontsize = 14, color = 'darkred']
}
")

```

The path analysis confirms that social responsibility perceptions significantly mediate the relationship between ControvPay exposure and customer loyalty, accounting for a reduction of 0.15 points in the loyalty scale [95% CI: -0.27, -0.04]. We will proceed with further analysis of this mediation effect's practical implications in Section X.



# Business Impact

Up to now, we have seen that the introduction of ControvPay can generate negative effects in the perceptions of social responsibility and loyalty of the retailers's customers. Yet, for taking decisions it was important to quantify how many customers we predicted to switch from a positive perception of social responsibility to a negative one, or from being a loyal customer to not. 

For these predictions, we will consider the neutral points of the scales as cut-points, especifically: 

* Scores below 4 in social responsibility perception, will be considered a negative one. 
* Scores below 4 in loyalty, will be considered to represent unloyal customers. 

For simplicity in the calculation of the metrics, we also create a dichotomous numeric variable about the experimental condition


```{r}

# Create the dicotomous variable accounting for negative social responsibility perception
customers.pay.df$neg.social.responsibility <- NA_real_
customers.pay.df$neg.social.responsibility [customers.pay.df$social.responsibility < 4] <- 1
customers.pay.df$neg.social.responsibility [customers.pay.df$social.responsibility >= 4] <- 0

# Create the dicotomous variable accounting for unloyal customers
customers.pay.df$unloyalty <- NA_real_
customers.pay.df$unloyalty [customers.pay.df$loyalty < 4] <- 1
customers.pay.df$unloyalty [customers.pay.df$loyalty >= 4] <- 0

# Create a dicotomous variable for the condition factor
customers.pay.df$controvpay <- NA_real_
customers.pay.df$controvpay [customers.pay.df$condition == "experimental"] <- 1
customers.pay.df$controvpay [customers.pay.df$condition == "control"] <- 0

# Check the distributions
summary(customers.pay.df)


```

We can see that 8% of the retailers' customers reported a negative perception of social responsibility, and 37% reported unloyalty. 

To predict how these scores would vary depending on the exposure to ControvPay, and the uncertainty of these predictions, we will use logistic binomial models and a function from our Toolkit to obtain predictive interpretation measures from these models. We specify the function below: 

```{r}
#####
#Function to obtain key interpretation metrics for a binomial logistic model
#####


f.metrics.binomial <- function(my.model, my.matrix){
  
  #--------1. Preliminary Checks: 
  
  # Making sure the model is glm binomial
  if (!inherits(my.model, "glm") || my.model$family$family != "binomial") {
    stop("The function requires a binomial model.")
  }
  
  
  #--------2. Odds Ratios
  
  # Obtaining the coefficients and confidence intervals
  coefs <- coef(my.model)
  ci <- confint(my.model)
  intercept <- coefs[1]
  
  # Exponentiation of the coefficients and their CIs to obtain odds ratios
  or <- exp(coefs)
  or_ci <- exp(ci)
  
  
  #--------3. Relative Probabilities (Risk Ratios)
  
  # Calculating the base probability from the intercept
  p0 <- or[1] / (1 + or[1])
  
  # Obtaining relative probabilities from risk ratios and base probability
  rp <- or / ((1 - p0) + (p0 * or))
  rp_ci_low <- or_ci[, 1] / ((1 - p0) + (p0 * or_ci[, 1]))
  rp_ci_high <- or_ci[, 2] / ((1 - p0) + (p0 * or_ci[, 2]))
  
  
  #--------4. Predicted Proportions
  
  # Extract log-odds and their sd for the individual presence of the factors (using the specified matrix)
  pred <- predict(my.model, newdata = my.matrix, type = "link", se.fit = TRUE)

  #Calculate confidence intervals in log-odds
  lower_logit <- pred$fit - 1.96 * pred$se.fit
  upper_logit <- pred$fit + 1.96 * pred$se.fit

  #Specify a function to transform log-odds to probabilities
  f.inv_logit <- function(x) {1 / (1 + exp(-x))}
  
  #Apply the function to the log-odds and the limits of their ci
  predicted_prob <- f.inv_logit(pred$fit) # Predicted probabilities
  lower_predicted_prob <- f.inv_logit(lower_logit) # Lower limit of CI for predicted probabilities
  upper_predicted_prob <- f.inv_logit(upper_logit) # Upper limit of CI for predicted probabilities

  
  #--------5. Differences in Predicted Probabilities via Bootstrap

  # Simulate a distribution of log-odds, for example with 10000 cases
  set.seed(123)
  simulated_log_odds <- as.data.frame(matrix(
  rnorm(10000 * length(pred$fit), mean = pred$fit, sd = pred$se.fit),
  ncol = length(pred$fit), 
  byrow = TRUE # the data is simulated line by line, so the values goes to the column of the corresponding factor
  ))

  # Transform logg-odds to expected probabilities (using the function specified above)
  simulated_probs <- f.inv_logit(simulated_log_odds)

  # Calculate differences from the first column, which correspond to the intercept probabilities
  diffs <- apply(simulated_probs, 2, function(col){
  col - simulated_probs[[1]]
  })

  # Calculate the means of the differences and 95% CI with percentiles
  prob_diff <- colMeans(diffs)
  lower_prob_diff  <- apply(diffs, 2, quantile, probs = 0.025)
  upper_prob_diff <- apply(diffs, 2, quantile, probs = 0.975)
  
  
  #-------- 6. Combine Results
  
  results <- data.frame(
    Term = names(rp),
    Prediction = as.numeric(predicted_prob)*100,
    Lower_Prediction = as.numeric(lower_predicted_prob)*100,
    Upper_Prediction = as.numeric(upper_predicted_prob)*100,
    Predicted_Change = as.numeric(prob_diff)*100,
    Lower_Predicted_Change = as.numeric(lower_prob_diff)*100,
    Upper_Predicted_Change = as.numeric(upper_prob_diff)*100,
    Relative_Probability = as.numeric(rp),
    Lower_Relative_Probability = as.numeric(rp_ci_low),
    Upper_Relative_Probability = as.numeric(rp_ci_high),
    Odds_Ratio = as.numeric(or),
    Lower_Odds_Ratio = as.numeric(or_ci[,1]),
    Upper_Odds_Ratio = as.numeric(or_ci[,2])
)
  
  # Remove meaningless metrics for intercept
  results[1, c("Predicted_Change",
             "Lower_Predicted_Change",
             "Upper_Predicted_Change",
             "Relative_Probability",
             "Lower_Relative_Probability",
             "Upper_Relative_Probability",
             "Odds_Ratio",
             "Lower_Odds_Ratio",
             "Upper_Odds_Ratio")] <- NA_real_

  
  # Return the results
  return(results)
}

```

After applying these specifications, we are ready to calculate the expected impact of adding ControvPay on the retailer's social responsibility perceptions and loyalty. 


## Impact on Social Responability Perception

To make predictions, we especified a binomial logistic model to predict social responsibility perception from the experimental condition within our customers dataframe, then obtained predictive measures. 

```{r}

# Specify the model
m.neg.social.responsibility <- glm (neg.social.responsibility ~ controvpay, data = customers.pay.df, family = "binomial")
summary(m.neg.social.responsibility)


#####
# Specify the design matrix for predictions
#####

# Extract the factor names from the model, with and without the intercept
f.names.interc <- names(coef(m.neg.social.responsibility))
f.names <- f.names.interc[-1]

# Create a matrix with 1s on the diagonal for each factor, 0 othewise
my.matrix.df <- as.data.frame(diag(length(f.names.interc)))
my.matrix.df[, 1] <- f.names.interc
names(my.matrix.df) <- c("case", f.names)

# Check the matrix structure
my.matrix.df


#####
# Calculate the model metrics
#####

metrics.neg.social.responsibility <- f.metrics.binomial (my.model = m.neg.social.responsibility, 
                                                         my.matrix = my.matrix.df)
metrics.neg.social.responsibility


```

We can see that the introduction of ControvPay is associated with a 4% increase of customers having negative perceptions of the social responsability of the retailer within the retailers' customer base. This comparison is also displayed in a graph in section x. 

## Impact on Loyalty

We followed a similar procedure as in the prior section to make predictions about loyalty: 
* We first specified the model to predict loyalty from the exposition to ControvPay
* Then specified a matrix that represents cases with the exposition to ControvPay or not
* Then obtained predictive metrics from the model and the matrix. 

```{r}

# Specify the model
m.unloyalty <- glm (unloyalty ~ controvpay, data = customers.pay.df, family = "binomial")
summary(m.unloyalty)


#####
# Specify the design matrix for predictions
#####

# Extract the factor names from the model, with and without the intercept
f.names.interc <- names(coef(m.unloyalty))
f.names <- f.names.interc[-1]

# Create a matrix with 1s on the diagonal for each factor, 0 othewise
my.matrix.df <- as.data.frame(diag(length(f.names.interc)))
my.matrix.df[, 1] <- f.names.interc
names(my.matrix.df) <- c("case", f.names)

# Check the matrix structure
my.matrix.df


#####
# Calculate the model metrics
#####

metrics.unloyalty <- f.metrics.binomial (my.model = m.unloyalty, 
                                                         my.matrix = my.matrix.df)
metrics.unloyalty


```

The introduction of ControvPay is expected to be associated with a 4.6 % decrease in loyal customers within the retailers' customer base. This comparison is also displayed in a graph in section x. 


# Visual Representation of the Impact


```{r}

# Merge the results
metrics.unloyalty$dep.variable <- "loyalty"
metrics.neg.social.responsibility$dep.variable <- "social.responsibility"
metrics.df <- bind_rows(metrics.neg.social.responsibility, metrics.unloyalty)
metrics.df

# Setting the order of the DVs
metrics.df$dep.variable <- factor(metrics.df$dep.variable, levels = c("social.responsibility", "loyalty"))

# Titles for each faceted graph representing each DV
custom_titles <- c(
  social.responsibility   = "Negative Perception of\nSocial Responsibility",
  loyalty    = "Disloyalty")


# Plotting the bar graph
ggplot(metrics.df, aes(x = Term, y = Prediction)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7, fill = "grey80") + 
  
  # Error bars
  geom_errorbar(
    aes(ymin = Lower_Prediction, ymax = Upper_Prediction),
    position = position_dodge(width = 0.8),
    width = 0.2) + 
  
  # Facets for each dv
  facet_wrap(~ dep.variable, 
             scales = "fixed", 
             axes = "all", 
             labeller = labeller(dep.variable = custom_titles),
             strip.position = "top") + 
  
  # Graph title and y title
   labs(
    y = "% of Customers", 
    title = "Expected Impact on Retailers' Customers") + 
  
  # x Titles
  scale_x_discrete(labels = c ("Current\nSituation", "After Adding\nControvPay")) + 
  
  # Limits in y axis
  ylim(0, 60) + 
  
  # Data labels
  geom_text(
    aes(y = Upper_Prediction, label = paste0(round(Prediction, 0), "%")), # label with percentage rounded
    position = position_dodge(width = 0.8),   # match the dodge of bars
    vjust = -1,                             # slightly above the bar
    size = 3.5                                # text size
  ) +
  
  # Formatting
  theme_minimal(base_size = 12) +
  theme(
    axis.title.x = element_blank(),
    strip.placement = "outside",
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    strip.text = element_text(face = "bold", size = 11), # the panel titles
    axis.text.x = element_text(angle = 0, vjust = 0, hjust = 0.5, size = 11),  
    plot.margin = margin(10, 5, 10, 5)
  )

```

In the graph we can see the changes that the introduction of ControvPay are expected to change on the retailers'  customers: 
* more customers with a negative perception of social responsability.
* more customers becoming unloyal, that is, saying that probably will not visit back the website again.

Even though these predictions are subject to error, and the error bars suggest that it would also be expected that the introduction of ControvPay will not produce any change, the most probable outcome is the negative one reflected by the percentages in the graph. 


# 9. Discussion

## 9.1. Managerial Implications

Our analysis suggest that, although ControvPay is the preferred payment option for 3% of the customers, its introduction is only expected to bring negative consequences to the business: 
* It is not expected to increase the intention to purchase nor the easiness of the payment process. 
* Within the retailer's customer base, it is expected to: 
  * increase in 4% the customers having negative image of the social responsability of the retailer
  * increase in 4.6% the unloyalty of customers, that is, those predicting not comming back. 
Attending to these risks and the absence of positive implications, we recommend to wait for the introduction of ControvPay until further evidence sugest more promising results. 


## 9.2. Limitations

It is important to recognize several limitations. First, the sample size was limited for the small effects that we found, which could have limit our power to identify other relevant effects on the intention to purchase or other methods for which we found no statistical differences. Second, the analyses are based on reported data in an unnatural environment: the presentation of the payment options in isolation. Evaluations with observational measures of real interactions in the web might produce different pattern of results. 


## 9.3. Next Steps

Future work could extend these analyses by:

* Evaluating the impact of including ControvPay with real interactions of customers in the retailer's website through A/B tests.

* Replications of this study with higher sample sizes. 

* Exploring heterogeneity across customer segments, to identify whether some groups are more sensitive to the ControvPay introduction.


# Appendix

To save the dataframes we can  use the code below

```{r}
write.csv(pay.df, "pay.df.csv")
```




