
---
title: "ANOVA. Frequentist and Bayesian Approach"
output:
  html_document:
    df_print: paged
    css: my_style.css
  html_notebook:
    css: my_style.css
  pdf_document: default
---
  
  
  
# Introduction  

This ANOVA toolkit includes reusable functions to conduct frequentist analyses across a group of dependent variables. It provides useful related analyses, including post-hoc Tukey tests, descriptive statistics, effect sizes, and graphs.

In addition, it includes functions to perform the ANOVA analyses with a Bayesian approach, with the possibility to specify different priors. 

# Setup

We start by loading the required packages for data manipulation and visualization. 

```{r}

# Visualization
library(ggplot2)     # General plotting

# Analysis
library(BayesFactor) # Bayesian Analysis

```

We also load the database used for the examples: 

```{r}
data <- read.csv("pay.df.csv")
summary(data)

```

# Frequentist Approach

## Anova with 2 Factors

### Reusable Function

This function allows to evaluate factorial ANOVAs with 2 factors across a variety of dependent variables in our dataset.  

```{r}

# Function for obtaining factorial ANOVA results for multiple DVs across 2 factors

# Function name: f.factorial.anova.2f
#
# Input parameters:
#   my.data: the dataframe
#   my.dv.list: vector of dependent variable names
#   my.factor1: first factor variable
#   my.factor2: second factor variable
#
# Output: list containing:
#   anova: ANOVA results for main effects and interactions, with effect sizes (eta squared)
#   descriptives: means, standard deviations, and 95% CI for all effects
#   tukey: post-hoc comparisons with Cohen's d effect sizes

f.factorial.anova.2f <- function (my.data, my.dv.list, my.factor1, my.factor2) {
  
  # Initialize lists for results storage
  anova.results <- list()    # ANOVA results
  descriptive.results <- list()  # Descriptive statistics
  cohen.d.results <- list()  # Cohen's d results
  tukey.results <- list()    # Tukey post-hoc results
  a <- d <- c <- t <- 1  # List indices for the lists above

  # Obtain factor levels
  f1.levels <- unique (my.data[[my.factor1]])
  f2.levels <- unique (my.data[[my.factor2]])
  
  # Specify function for Cohen d calculation
    f.cohen.d.calculation <- function (groups.data, groups.matrix, dv.name, effect.name, level.names) {
    
      # Create a list to store the results
      fd.results.list <- list()
      fd <- 1 # index for the above list
    
      # Open a loop for each comparison
      for (i.comparison in 1:nrow(groups.matrix)){
      
        # Obtain the group indexes to compare
        index.g1 <- groups.matrix [i.comparison, 1]
        index.g2 <- groups.matrix [i.comparison, 2]
      
        # Obtain the names of groups compared
        name.g1 <- groups.data [index.g1, level.names]
        name.g2 <- groups.data [index.g2, level.names]
      
        # Obtain the means of groups compared
        mean.g1 <- groups.data [index.g1, "mean"]
        mean.g2 <- groups.data [index.g2, "mean"]
      
        # Obtain the sd of groups compared
        sd.g1 <- groups.data [index.g1, "sd"]
        sd.g2 <- groups.data [index.g2, "sd"]
      
        # Obtain the n of groups compared
        n.g1 <- groups.data [index.g1, "n"]
        n.g2 <- groups.data [index.g2, "n"]     
      
        # Calculate the pooled standard deviation
        pooled.sd <- sqrt(((n.g1 - 1) * sd.g1^2 + (n.g2 - 1) * sd.g2^2) / (n.g1 + n.g2 - 2))
      
        # Calculate Cohen's d
        cohen.d <- (mean.g1 - mean.g2)/ pooled.sd
      
        # Save the results for each comparison
        comparison.cohen.d.result <- data.frame (
          dep.variable = dv.name,
          effect = effect.name,
          group1 = name.g1,
          group2 = name.g2,
          d = cohen.d, 
          sd.pooled = pooled.sd
        )
        fd.results.list [[fd]] <- comparison.cohen.d.result
        fd <- fd + 1
      
      } # Close the loop within the f.cohen.d.calculation   
      
      d.function.results <- do.call(rbind, fd.results.list)
      
    # Return the result for the effect
    return (d.function.results)
   
    } # Close the f.cohen.d.calculation function
      
  # Initiate a loop for each dv
  for (dv in my.dv.list) {
    
    
#--- 1. Metrics for the ANOVA models
    
    # Build a dynamic formula
    anova.formula <- as.formula (paste0(dv, "~", my.factor1, "*", my.factor2))

    # Fit the ANOVA model
    anova.model <- aov(anova.formula, data = my.data)
    
    # Extract the model in a dataframe
    anova.table <- anova(anova.model)
    
    # Bind the anova table with a dataframe that contains the dv names
    anova.result.df <- data.frame (dep.variable = rep(dv, nrow(anova.table)), 
                                    effect = rownames(anova.table))
    anova.result.df <- bind_cols (anova.result.df, anova.table)
    
    # Add the eta squared (Proportional Reduction in Error)
    ss.total <- sum(anova.table[ , "Sum Sq"]) # sum of error
    anova.result.df$eta.squared <- anova.result.df[["Sum Sq"]] / ss.total
    
    # Save the results
    anova.results [[a]] <- anova.result.df
    a <- a + 1
    
 
    
#--- 2. Posthoc Comparison with Tukey
    
    # Obtain the Tukey results
    tukey <- TukeyHSD(anova.model)
    
    # Bind the comparisons for main effects and interaction effects in a single dataframe
    for (name.effect in names(tukey)) {
      
      # Extract the comparisons for the effect
      tukey.df <- as.data.frame(tukey[[name.effect]])
      tukey.df$dep.variable <- dv
      tukey.df$effect <- name.effect
      tukey.df$comparison <- rownames(tukey.df)
      tukey.results [[t]] <- tukey.df
      t <- t + 1
    } # Close the loop for the Tukey effect       
    
    
    
#--- 3. Descriptive Statistics
    
    # -- 3.1. Descriptives for factor 1
    
    # Open a loop for factor 1
    for (f1.level in f1.levels){
      
      # Create a vector with the scores of each level in factor 1
      current.vector <- my.data[my.data[[my.factor1]] == f1.level , dv]
      
      # Clean missind data
      current.vector.c <- current.vector[!is.na(current.vector)]
      
      # Obtain the mean, standard deviations, standard errors, n, and 95% CI
      mean.level <- mean(current.vector.c)
      sd.level <- sd(current.vector.c)
      n.level <- length(current.vector.c)
      se.level <- sd.level / sqrt(n.level)
      upper.ci.level <- mean.level + 1.96 * se.level
      lower.ci.level <- mean.level - 1.96 * se.level
      
      # Save the results
      level.descriptive.results <- data.frame (
        dep.variable = dv, 
        factor1.levels = f1.level,
        factor2.levels = paste0 ("all"),
        mean = mean.level,
        sd = sd.level,
        upper.ci = upper.ci.level,
        lower.ci = lower.ci.level,
        se = se.level,
        n = n.level, 
        level.name = f1.level)
      
      
      descriptive.results[[d]] <- level.descriptive.results
      d <- d + 1
    
    } # Close the loop for factor 1
     
    
    # -- 3.2. Descriptives for factor 2
      
    # Open a loop for factor 2
    for (f2.level in f2.levels){
      
      # Create a vector with the scores of each level in factor 2
      current.vector <- my.data[my.data[[my.factor2]] == f2.level , dv]
      
      # Clean missind data
      current.vector.c <- current.vector[!is.na(current.vector)]
      
      # Obtain the mean, standard deviations, standard errors, n, and 95% CI
      mean.level <- mean(current.vector.c)
      sd.level <- sd(current.vector.c)
      n.level <- length(current.vector.c)
      se.level <- sd.level / sqrt(n.level)
      upper.ci.level <- mean.level + 1.96 * se.level
      lower.ci.level <- mean.level - 1.96 * se.level
      
      # Save the results
      level.descriptive.results <- data.frame (
        dep.variable = dv, 
        factor1.levels = paste0 ("all"),
        factor2.levels = f2.level,
        mean = mean.level,
        sd = sd.level,
        upper.ci = upper.ci.level,
        lower.ci = lower.ci.level,
        se = se.level,
        n = n.level,
        level.name = f2.level
      )
      
      descriptive.results[[d]] <- level.descriptive.results
      d <- d + 1
      
      } # Close the loop for factor 2
    
    
    # -- 3.3. Descriptives for the interaction
    
      # Open loops for the interaction

      for (f1.level in f1.levels){
        for (f2.level in f2.levels){
      
        # Create a vector with the scores of the interaction level
        current.vector <- my.data [my.data[[my.factor1]] == f1.level &  my.data[[my.factor2]] == f2.level, dv ]
      
        # Clean missind data
        current.vector.c <- current.vector[!is.na(current.vector)]
      
        # Obtain the mean, standard deviations, standard errors, n, and 95% CI
        mean.level <- mean(current.vector.c)
        sd.level <- sd(current.vector.c)
        n.level <- length(current.vector.c)
        se.level <- sd.level / sqrt(n.level)
        upper.ci.level <- mean.level + 1.96 * se.level
        lower.ci.level <- mean.level - 1.96 * se.level
      
        # Save the results
        level.descriptive.results <- data.frame (
        dep.variable = dv, 
        factor1.levels = f1.level,
        factor2.levels = f2.level,
        mean = mean.level,
        sd = sd.level,
        upper.ci = upper.ci.level,
        lower.ci = lower.ci.level,
        se = se.level,
        n = n.level,
        level.name = paste0(f1.level, ":", f2.level)
      )
      
      descriptive.results[[d]] <- level.descriptive.results
      d <- d + 1
    
    } # Close the loop of factor 1 in the interaction loops
      }  # Close the loop of factor 2 in the interaction loop
    
    
# --- 4. Cohen's d Calculations
    
    # -- 4.1. Cohen's d for factor 1 comparisons
    
    # Extract the descriptives for factor 1
    data.groups.to.compare <- do.call(rbind, descriptive.results)
    data.groups.to.compare <- data.groups.to.compare[data.groups.to.compare$dep.variable == dv & 
                                   data.groups.to.compare$factor2.levels == "all", ]
    
    # Obtain the number of groups
    n.groups <- nrow(data.groups.to.compare)
    
    # Obtain a matrix with the group combination indexes
    comparison.matrix <- as.data.frame(t(combn(1:n.groups, 2)))
    
    # Apply the f.cohen.d.calculation function to calculate the d results for factor 1
    factor1.d.results <- f.cohen.d.calculation(
      groups.data = data.groups.to.compare,
      groups.matrix = comparison.matrix,
      dv.name = dv,
      effect.name = my.factor1, 
      level.names = "level.name"
    )
    
    # Save the d results for the factor 1  groups
    cohen.d.results[[c]] <- factor1.d.results
    c <- c + 1
    
    
    # -- 4.2. Cohen's d for factor 2 comparisons
    
    # Extract the descriptives for factor 2
    data.groups.to.compare <- do.call(rbind, descriptive.results)
    data.groups.to.compare <- data.groups.to.compare[data.groups.to.compare$dep.variable == dv & 
                                   data.groups.to.compare$factor1.levels == "all", ]
    
    # Obtain the number of groups
    n.groups <- nrow(data.groups.to.compare)
    
    # Obtain a matrix with the group combination indexes
    comparison.matrix <- as.data.frame(t(combn(1:n.groups, 2)))
    
    # Apply the f.cohen.d.calculation function to calculate the d results for factor 2
    factor2.d.results <- f.cohen.d.calculation(
      groups.data = data.groups.to.compare,
      groups.matrix = comparison.matrix,
      dv.name = dv,
      effect.name = my.factor2,
      level.names = "level.name"
    )    
    
    # Save the d results for the factor 2  groups
    cohen.d.results[[c]] <- factor2.d.results
    c <- c + 1  
    

    # -- 4.3. Cohen's d for the interaction comparisons
    
    # Extract the descriptives for the interaction
    data.groups.to.compare <- do.call(rbind, descriptive.results)
    data.groups.to.compare <- data.groups.to.compare[data.groups.to.compare$dep.variable == dv & 
                                  data.groups.to.compare$factor1.levels != "all" &
                                  data.groups.to.compare$factor2.levels != "all", 
                                  ]
    
    # Obtain the number of groups
    n.groups <- nrow(data.groups.to.compare)
    
    # Obtain a matrix with the group combination indexes
    comparison.matrix <- as.data.frame(t(combn(1:n.groups, 2)))
    
    # Apply the f.cohen.d.calculation function to calculate the d results for the interaction
    interaction.d.results <- f.cohen.d.calculation(
      groups.data = data.groups.to.compare,
      groups.matrix = comparison.matrix,
      dv.name = dv,
      effect.name = paste0(my.factor1, ":", my.factor2),
      level.names = "level.name"
    )    
    
    # Save the d results for the factor 2  groups
    cohen.d.results[[c]] <- interaction.d.results
    c <- c + 1  
    

    
} # close the dv loop
  

    
#--- 5. Save all the results

  
  #--- ANOVA Results
  
  # Group the anova results in a dataframe
  anova.results.df <- do.call(rbind, anova.results)
  rownames(anova.results.df) <- NULL
  
  # Round the data columns
  numeric.cols <- sapply(anova.results.df, is.numeric)
  anova.results.df[numeric.cols] <- round(anova.results.df[numeric.cols], 3)
  
  
  #--- Descriptive Results
  
  # Group the descriptives for all levels
  descriptives.df <- do.call(rbind, descriptive.results)
  
  # Round the columns
  numeric.cols <- sapply(descriptives.df, is.numeric)
  descriptives.df[numeric.cols] <- round(descriptives.df[numeric.cols], 2)
  
  # Rename the factor columns
  names (descriptives.df)[names(descriptives.df) == "factor1.levels"] <- my.factor1
  names (descriptives.df)[names(descriptives.df) == "factor2.levels"] <- my.factor2
  
  
  #--- Cohen's d Results
  
  # Group the d results for all comparisons
  cohen.d.df <- do.call(rbind, cohen.d.results)
  
  # Add a "comparison" variable" to use as a key for the Tukey results, duplicating all comparisons with the altered order
  cohen.d.df1 <- cohen.d.df
  cohen.d.df1$comparison <- paste0 (cohen.d.df1$group1, "-", cohen.d.df1$group2)
  cohen.d.df2 <- cohen.d.df
  cohen.d.df2$comparison <- paste0 (cohen.d.df2$group2, "-", cohen.d.df2$group1)
  cohen.d.df2$d <- cohen.d.df2$d *(-1)
  doubled.cohen.d.df <- bind_rows(cohen.d.df1, cohen.d.df2)
  
  
  #--- Tukey Results
  
  # Group all the Tukey results
  tukey.results.df <- do.call(rbind, tukey.results)
  rownames(tukey.results.df) <- NULL
  
  # Reorder the columns
  index.tukey <- tukey.results.df [ , c("dep.variable", "effect", "comparison")]
  tukey.results.df[ , c("dep.variable", "effect", "comparison")] <- NULL
  tukey.results.df <- bind_cols(index.tukey, tukey.results.df)
  
  # Add the Cohen's d results
  tukey.results.df <- merge(tukey.results.df, doubled.cohen.d.df, by = c("dep.variable", "effect", "comparison"), all.x = TRUE)
  tukey.results.df$group1 <- NULL
  tukey.results.df$group2 <- NULL

  #--- List with all the results
  
  results <- list(anova = anova.results.df, 
                  descriptives = descriptives.df,
                  cohen.d = cohen.d.df,
                  tukey = tukey.results.df)
  
  # Return the results
  return(results)

}

```

### Example of Usage: 

This example uses the **pay.df** dataframe, based on the project: "Corporate responsibility Versus Easiness of E-Commerce Payments Methods: An Experimental Study."

We applied the function to analyze the following variables: 
 * **DVs:** Questionnaire scores for social responsibility perception, ease perceptions, purchase intention, and loyalty.
 * **Factor 1 (`condition`):** Two experimental groups (control vs. ControvPay exposition).
 * **Factor 2 (`customer`):** Whether participants were customers ("yes") or non-customers ("no") of the retailer.

```{r}

# Vector of dependent variable names
dv.variables <- c("social.responsibility", "ease", "purchase.intention", "loyalty")

# Application of ANOVA function
pay.results <- f.factorial.anova.2f(
  my.data = pay.df,
  my.dv.list = dv.variables,
  my.factor1 = "condition",
  my.factor2 = "customer"
)

# Extract ANOVA results
pay.anova.df <- pay.results$anova
pay.anova.df

# Extract descriptive statistics
pay.descriptives.df <- pay.results$descriptives
pay.descriptives.df

# Extract post-hoc comparisons
pay.tukey.df <- pay.results$tukey
pay.tukey.df

```


### Example for Plotting Results

Let's suppose we are interested in plotting the interaction effect. We can visualize it with a bar graph:

```{r}

# Select interaction descriptives for graphing
pay.descriptives.int.df <- pay.descriptives.df [!(pay.descriptives.df$condition == "all") & !(pay.descriptives.df$customer =="all"), ]

# Specify the order of the DVs
pay.descriptives.int.df$dep.variable <- factor(pay.descriptives.int.df$dep.variable, levels = c("ease", "social.responsibility", "purchase.intention", "loyalty"))

# Custom titles for faceted graphs
custom_titles <- c(
  social.responsibility   = "Social Responsibility Perception",
  ease     = "Ease Perception",
  purchase.intention = "Purchase Intention",
  loyalty   = "Loyalty"
)

# Bar graph visualization
ggplot(pay.descriptives.int.df, aes(x = condition, y = mean, fill = customer)) + 
  
  # Type of graph
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +  
  
  # Error bars
  geom_errorbar(
    aes(ymin = lower.ci, ymax = upper.ci),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) + 
  
  # Facets
  facet_wrap(~ dep.variable, 
             scales = "fixed", 
             axes = "all", #
             labeller = labeller(dep.variable = custom_titles)) + 
  
  # Graph title, axis titles, and fill title
  labs(
    y = "Mean Scores",
    x = "Experimental Condition",
    fill = "Customer",
    title = "Differences Across Experimental Conditions"
  ) + 
  
  # Labels in x axis
  scale_x_discrete(labels = c ("No ControvPay", "ControvPay")) + 
  
  # Data labels
  geom_text(
    aes(y = upper.ci, label = paste0(round(mean, 2))), # use upper ci as reference position
    position = position_dodge(width = 0.8),   # match the dodge of bars
    vjust = -0.5,                             # slightly above the bar
    size = 2.5                                # text size
  ) + 
  
  # Limits for the y axis
  coord_cartesian(ylim = c(3, 6.2)) +  
  
  # Formatting
  theme_minimal(base_size = 12) +
    theme(
    axis.title.x = element_blank(),
    legend.position = "right",
    legend.justification = c("right", "bottom"),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text  = element_text(size = 10),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    strip.text = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, vjust = 0, hjust = 0.5),  
    plot.margin = margin(10, 5, 10, 5)
  ) 

```

# Bayesian Approach

## Reusable Function for Bayesian ANOVA

This function provides Bayesian ANOVA analyses for a list of dependent variables and factors, with the option to specify different priors.  

```{r}

# Function for Bayesian ANOVA with multiple priors

# Function name: f.bayes.anova
#
# Input parameters:
#   my.data: dataframe containing the variables
#   my.dv.list: vector of dependent variable names
#   my.factor.list: vector of factor variable names  
#   my.priors: vector of prior scales to test
#
# Output: list containing:
#   individual models for each DV and prior combination
#   summary: consolidated results dataframe

f.bayes.anova <- function (my.data, my.dv.list, my.factor.list, my.priors){
  
  # Initialize results storage
  bayes.results <- list()  
  summary.bayes.results <- list()
  p <- 1 # index for summary.bayes.results
  
  # Construct formula from factor list
  factor.formula = paste0 ("~ ")
    for (i.factor in seq_along(my.factor.list)){
      if (i.factor != length(my.factor.list)) {
           factor.formula <-  paste0 (factor.formula, my.factor.list[i.factor], " * ")      
      } # Close the "if" function
           else {
             factor.formula <-  paste0 (factor.formula, my.factor.list[i.factor])
           }  # Close the "else" function
  } # Close the loop for the factors
  
  
  # Loop through DVs and priors
  for (dv in my.dv.list) {
    
    for(prior in my.priors) {
      
      # Fit Bayesian ANOVA model
      bayes.model <- anovaBF(as.formula(paste(dv, factor.formula)),
                      data = my.data,
                      rscaleFixed = prior,  
                      whichModels = 'all'
      )
      
      # Store model with descriptive name
      model.name <- paste0  (dv, ".prior.", prior)
      bayes.results[[model.name]] <- bayes.model
      
      # Create summary dataframe
      model.df <- as.data.frame (bayes.model)
      model.df$dep.variable <- dv
      model.df$prior <- prior
      model.df$effect <- row.names(model.df)
      model.df$BF <- model.df[[1]]
      model.df$error <- model.df[[2]]
      model.df <- model.df [ , c("dep.variable", "prior", "effect", "BF", "error")]
      
      # Save the summary dataframe
      summary.bayes.results [[p]] <- model.df
      p <- p  + 1 
      
    } # Close the loop for the priors
    
  } # Close the loop for the DVs
  
  # Consolidate results
  summary.df <- do.call(rbind, summary.bayes.results)
  row.names(summary.df) <- NULL
  bayes.results[["summary"]] <- summary.df
  
  return(bayes.results)
  
}

```


## Example of Usage

This example uses the **pay.df** dataframe, based on the project: "Corporate responsibility Versus Easiness of E-Commerce Payments Methods: An Experimental Study."

We applied the function to analyze the following variables: 
 * **DVs:** Questionnaire scores for social responsibility perception and loyalty.
 * **Factor 1 (`condition`):** Two experimental groups (control vs. ControvPay exposition).
 * **Factor 2 (`customer`):** Whether participants were customers ("yes") or non-customers ("no") of the retailer.

We tested multiple prior scales (r = 0.1, 0.5, 1). 

```{r}

# Specify priors for sensitivity analysis
priors <- c(0.1, 0.5, 1)

# Dependent variables for Bayesian analysis
dvs <- c("social.responsibility", "loyalty")

# Experimental factors
factors <- c("condition", "customer")

# Apply Bayesian ANOVA function
bayes.anova.results <- f.bayes.anova(my.data = pay.df, 
                                    my.dv.list = dvs, 
                                    my.factor.list = factors, 
                                    my.priors = priors)

# Display results summary
summary.bayes <- bayes.anova.results[["summary"]]
summary.bayes

```

## Example of Interpretation

For loyalty, the evidence consistently supported the absence of an interaction effect across all priors. While this conclusion is currently supported by anecdotal to moderate evidence, it suggests that ControvPay is unlikely to substantially impact customer loyalty.

For social responsibility, the results present ambiguous evidence regarding an interaction effect. With more conservative priors (rscale = 0.5 or 1.0), the evidence favored the null hypothesis of no differential effect between experimental conditions across customer profiles. However, these priors are less sensitive to detecting small effects. Conversely, when using a more sensitive prior (rscale = 0.1), we found anecdotal evidence for an interaction effect, though such sensitive priors also increase the risk of detecting statistical noise.

Given that even small decreases in social responsibility perceptions could be impactful for our large-scale retailer, we proceeded to quantify this potential effect using Monte Carlo simulation to estimate the practical significance of this ambiguous finding.


```{r}

# Extract the model for social responsibility with sensitive prior
m.soc.resp.0.1 <- bayes.anova.results[["social.responsibility.prior.0.1"]]

# Simulate Monte Carlo chains
chain.bayes.social.responsibility <- posterior(m.soc.resp.0.1, 
                                               index = 7, 
                                               iterations = 10000)

# Convergence diagnostics for Monte Carlo chains
plot(chain.bayes.social.responsibility[, 1:10])

# Inspect Monte Carlo chains
summary(chain.bayes.social.responsibility)

# Calculate posterior distributions for group means

# Main effects distributions
d.main.effects <- data.frame(chain.bayes.social.responsibility[, 2:5] + chain.bayes.social.responsibility[, 1])

# Interaction group distributions
d.control.yes <- chain.bayes.social.responsibility[, "mu"] + 
                 chain.bayes.social.responsibility[, "condition-control"] +
                 chain.bayes.social.responsibility[, "customer-yes"] + 
                 chain.bayes.social.responsibility[, "condition:customer-control.&.yes"]

d.control.no <- chain.bayes.social.responsibility[, "mu"] + 
                chain.bayes.social.responsibility[, "condition-control"] +
                chain.bayes.social.responsibility[, "customer-no"] + 
                chain.bayes.social.responsibility[, "condition:customer-control.&.no"]

d.experimental.yes <- chain.bayes.social.responsibility[, "mu"] + 
                      chain.bayes.social.responsibility[, "condition-experimental"] +
                      chain.bayes.social.responsibility[, "customer-yes"] + 
                      chain.bayes.social.responsibility[, "condition:customer-experimental.&.yes"]

d.experimental.no <- chain.bayes.social.responsibility[, "mu"] + 
                     chain.bayes.social.responsibility[, "condition-experimental"] +
                     chain.bayes.social.responsibility[, "customer-no"] + 
                     chain.bayes.social.responsibility[, "condition:customer-experimental.&.no"]

# Combine all posterior distributions
estimations <- bind_cols(as.data.frame(d.main.effects), 
                         condition.control_customer.yes = d.control.yes, 
                         condition.control_customer.no = d.control.no, 
                         condition.experimental_customer.yes = d.experimental.yes, 
                         condition.experimental_customer.no = d.experimental.no)

# Calculate 95% credible intervals
credible.intervals.soc.resp <- t(apply(estimations, 2, quantile, probs = c(0.025, 0.5, 0.975)))

# Save credible intervals in dataframe
credible.intervals.soc.resp.df <- data.frame(
  group = rownames(credible.intervals.soc.resp),
  median = credible.intervals.soc.resp[, "50%"],
  lower.ci = credible.intervals.soc.resp[, "2.5%"],
  upper.ci = credible.intervals.soc.resp[, "97.5%"]
)

rownames(credible.intervals.soc.resp.df) <- NULL
credible.intervals.soc.resp.df

```

The convergence diagnostics indicate that the model estimations were stable and converged appropriately (homogeneous patterns in the trace plots and normal distributions of the simulation results). The estimated means and credible intervals are consistent with the descriptive data. For better interpretation, we visualize them below.


## Graph Example 

We can create a dots-and-wisker plot to represent the above estimations and credible intervals

```{r}

# Visualization of posterior distributions
ggplot(credible.intervals.soc.resp.df, aes(x = group, y = median)) +
  
  # Graph type, confidence intervals
  geom_pointrange(aes(ymin = lower.ci, ymax = upper.ci), 
                  size = 0.7, color = "black") +
  
  # Formatting of points
  geom_point(size = 2, color = "black") +
  
  # Graph titles and Axis Titles
  labs(title = "Posterior Distributions - Social Responsibility Perception",
       subtitle = "Points show median estimates, bars show 95% credible intervals",
       y = "Social Responsibility Score (1-7 scale)", 
       x = "Experimental Group") +
  
  # Formatting
  theme_bw() +
  coord_flip() +
  theme(plot.title = element_text(face = "bold"),
        plot.subtitle = element_text(color = "gray40"))

```

## Example of Graph Interpretation

The posterior distributions provide evidence of the interaction we have been exploring: ControvPay differentially affects existing customers versus non-customers:

* Non-customers: Negligible difference (0.01 points) between those exposed and not exposed to ControvPay
* Existing customers: Decrease of 0.21 points in social responsibility perception when exposed to ControvPay

While the effect size is small, it could be meaningful given the large customer base. To further investigate this difference, we specifically evaluated the contrast between experimental conditions within the customer group using Bayesian post-hoc comparisons.

# Example of Bayesian ANOVA Post-Hoc Analysis

```{r}

# Calculate posterior distribution of differences within customers
dif.in.customers <- d.control.yes - d.experimental.yes

# Calculate credible intervals for the difference
ci.dif.in.customers <- quantile(dif.in.customers, probs = c(0.025, 0.5, 0.975))
ci.dif.in.customers

```

The results confirm that social responsibility perception is significantly lower for the retailer's customers exposed to ControvPay compared to those not exposed [median difference = 0.21 points, 95% CI: 0.03, 0.41].

The emergence of this difference specifically among existing customers aligns with theoretical expectations, as the retailer is known for high ethical standards, and its customers are likely more sensitive to ethical controversies in payment methods.

Given that social responsibility perception was associated with impactful outcomes like customer loyalty and purchase intention, we conducted mediation analyses within the customer subgroup to examine whether the effect on social responsibility had downstream consequences.



