---
title: "Percentages with CI across Multiple Variables and Subgroups"
output: html_notebook
---


# 1. Functions

## Percentages & CI for a List of Dichotomous DVs and 2 Grouping Factors

* Expected Outcome: a dataframe with columns for percentages and 95% CI limits for all dvs and subgroups specified

* Input: 
  * The original dataframe (my.data).
  * The name of a vector that lists the dependent variables of interest (that vector has to contain the variable names as character strings). 
  * The names of the factors used for the subgroups (my.factor1, my.factor2), as character strings. 

```{r}
f.prop.2f <- function(my.data, my.dv.list, my.factor1, my.factor2){
  
  # Initialize an empty list to store the sampled subsets from each stratum.
  results <- list() 
  
  # Initialize a counter for indexing elements in the 'results' list.
  p <- 1 
  
  # Obtain the levels of the factors
  f1.levels <- unique (my.data[[my.factor1]])
  f2.levels <- unique (my.data[[my.factor2]])
  
  #Create a loop for each dv and for each level of the factors
    for (dv in my.dv.list){
      for (lf1 in f1.levels){
        for(lf2 in f2.levels){
          
          # Extract the vector, successes and number of cases
          current.vector <- my.data[my.data[[my.factor1]]==lf1 & my.data[[my.factor2]]==lf2, dv]
          current.vector.c <- as.numeric(current.vector[!is.na(current.vector)]) #cleaning missing cases
          n <- length(current.vector.c) # number of cases in the vector
          s <- length(current.vector.c[current.vector.c == 1]) # number of cases satisfying the condition
          
          # Calculate proportions and their 95% CI
          if(n > 0){
            proportion <- s / n #calculating proportions
            binomial.test <- binom.test (s, n) # binomial test to calculate 95% CI of the proportions
            ci_lower <- binomial.test$conf.int[1] #extracting the lower limit of the CI
            ci_upper <- binomial.test$conf.int[2] #extracting the upper limit of the CI    
          }else{
            proportion <- NA
            ci_lower <- NA
            ci_upper <- NA
          }

          # Save the results in a named vector
          results [[p]] <- data.frame(dep.variable = dv, factor1 = lf1, factor2 = lf2, percentage = proportion * 100, 
                           ci_lower.perc = ci_lower * 100, ci_upper.perc = ci_upper * 100, stringsAsFactors = FALSE)
          p <- p + 1 
          
        } # close the loop for factor 2
      } # close the loop for factor 1
    } # close the loop for the dv

  #Combine the results in a dataframe and convert outcomes to numeric columns
  results.df <- (do.call(rbind, results))
  rownames(results.df) <- NULL

  #Return the dataframe
  return(results.df)
}
```

* Example of Usage: 

```{r}
prop.df <- f.prop.2f (my.data = data.complaints , my.dv.list = dv.variables, my.factor1 = "method", my.factor2 = "reason.grouped")

```

