---
title: "Percentages with CI across Multiple Variables and Subgroups"
output: html_notebook
---


# 1. Functions

## Percentages & CI for a List of Dichotomous DVs and 2 Grouping Factors

* Expected Outcome: a dataframe with columns for percentages and 95% CI limits for all dvs and subgroups specified

* Input: 
  * The original dataframe (my.data).
  * The name of a vector that lists the dependent variables of interest (that vector has to contain the variable names as character strings). 
  * The names of the factors used for the subgroups (my.factor1, my.factor2), as character strings. 

```{r}
f.prop.2f <- function(my.data, my.dv.list, my.factor1, my.factor2){
  
  # Initialize an empty list to store the sampled subsets from each stratum.
  results <- list() 
  
  # Initialize a counter for indexing elements in the 'results' list.
  p <- 1 
  
  # Obtain the levels of the factors
  f1.levels <- unique (my.data[[my.factor1]])
  f2.levels <- unique (my.data[[my.factor2]])
  
  #Create a loop for each dv and for each level of the factors
    for (dv in my.dv.list){
      for (lf1 in f1.levels){
        for(lf2 in f2.levels){
          
          # Extract the vector, successes and number of cases
          current.vector <- my.data[my.data[[my.factor1]]==lf1 & my.data[[my.factor2]]==lf2, dv]
          current.vector.c <- as.numeric(current.vector[!is.na(current.vector)]) #cleaning missing cases
          n <- length(current.vector.c) # number of cases in the vector
          s <- length(current.vector.c[current.vector.c == 1]) # number of cases satisfying the condition
          
          # Calculate proportions and their 95% CI
          if(n > 0){
            proportion <- s / n #calculating proportions
            binomial.test <- binom.test (s, n) # binomial test to calculate 95% CI of the proportions
            ci_lower <- binomial.test$conf.int[1] #extracting the lower limit of the CI
            ci_upper <- binomial.test$conf.int[2] #extracting the upper limit of the CI    
          }else{
            proportion <- NA
            ci_lower <- NA
            ci_upper <- NA
          }

          # Save the results in a named vector
          results [[p]] <- data.frame(dep.variable = dv, factor1 = lf1, factor2 = lf2, percentage = proportion * 100, 
                           ci_lower.perc = ci_lower * 100, ci_upper.perc = ci_upper * 100, stringsAsFactors = FALSE)
          p <- p + 1 
          
        } # close the loop for factor 2
      } # close the loop for factor 1
    } # close the loop for the dv

  #Combine the results in a dataframe and convert outcomes to numeric columns
  results.df <- (do.call(rbind, results))
  rownames(results.df) <- NULL

  #Return the dataframe
  return(results.df)
}
```

* Example of Usage: 

```{r}
prop.df <- f.prop.2f (my.data = data.complaints , my.dv.list = dv.variables, my.factor1 = "method", my.factor2 = "reason.grouped")

```

We can use a bar graph to depict the results, e.g.: 



```{r}

# Setting the order of the complaints variables
prop.df$dep.variable <- factor(prop.df$dep.variable, levels = c("complain.connect", "complain.repeat", "complain.sp.respond", "complain.sp.solve", "complain.other"))

# Titles for each faceted graph representing a type of complaint
custom_titles <- c(
  complain.connect   = "Connection Problems",
  complain.repeat     = "Need to Repeat Information",
  complain.sp.respond = "Slow Responses",
  complain.sp.solve   = "Slow Resolution",
  complain.other      = "Other Complaints"
)

# Plotting the bar graph
ggplot(prop.df, aes(x = factor1, y = percentage, fill = factor2)) +
  geom_col(position = position_dodge(width = 0.8), width = 0.7) +
  geom_errorbar(
    aes(ymin = ci_lower.perc, ymax = ci_upper.perc),
    position = position_dodge(width = 0.8),
    width = 0.2
  ) +
  facet_wrap(~ dep.variable, 
             scales = "fixed", 
             axes = "all", 
             labeller = labeller(dep.variable = custom_titles)) +
  labs(
    y = "% of Complaints",
    fill = "Country",
    title = "% of Chat Complaints by Issue Type"
  ) +
  scale_x_discrete(labels = c ("incorrect item", "other issue")) +
  ylim(0, 100) +  
  geom_text(
    aes(label = paste0(round(percentage, 0), "%")),         # label with percentage rounded
    position = position_dodge(width = 0.8),   # match the dodge of bars
    vjust = -3,                             # slightly above the bar
    size = 2.5                                # text size
  ) +
  theme_minimal(base_size = 12) +
  theme(
    axis.title.x = element_blank(),
    legend.position = c(1, 0),
    legend.justification = c("right", "bottom"),
    legend.title = element_text(size = 10, face = "bold"),
    legend.text  = element_text(size = 10),
    panel.spacing = unit(1, "lines"),
    plot.title = element_text(hjust = 0.5, face = "bold"),
    strip.text = element_text(face = "bold"),
    axis.text.x = element_text(angle = 0, vjust = 0, hjust = 0.5),  
    plot.margin = margin(10, 5, 10, 5)
  )
```

